---
output: html_document
editor_options: 
  chunk_output_type: console
---
# Bayesian Hierarchial Spatial Province Models for _P. vivax_ among Asymptomatic Adults in the DRC"


```{r, include=FALSE}
knitr::opts_chunk$set(echo = T, warning = F, message = F, eval = T, results = 'hide',
                      fig.align = 'center', fig.width = 8, fig.height = 8)
knitr::opts_knit$set(root.dir = here::here())
```

```{r}
#..............................................................
# dependencies
#..............................................................
source("~/Documents/GitHub/VivID_Epi/R/00-functions_basic.R") 
source("~/Documents/GitHub/VivID_Epi/R/00-functions_epi.R") 
source("~/Documents/GitHub/VivID_Epi/R/00-MCMC_diagnostics.R")
library(tidyverse)
library(srvyr) #wrap the survey package in dplyr syntax
library(CARBayes)
library(HDInterval)
library(raster)
set.seed(48)
```



## Hierarchial Bayesian Spatial Models for Province Prevalence 
### Make Model Framework
NB. When $\rho$ is `NULL`, it is estimated within the CAR model. based on the _Leroux et al. 2000_ specifiation of the Gaussian Markov Random Field.
```{r}
#......................
# Import Data
#......................
dt <- readRDS("data/derived_data/vividepi_recode_completecases.rds")
dtsrvy <- makecd2013survey(survey = dt)
ge <- readRDS(file = "data/raw_data/dhsdata/VivIDge.RDS")
DRCprov <- readRDS("data/map_bases/vivid_DRCprov.rds") %>% 
  dplyr::select(c("adm1name", "geometry"))

#------------------------------------------------------------------------
# Subset to Pv
#------------------------------------------------------------------------
pvprov.weighted <- dtsrvy %>% 
  dplyr::mutate(count = 1) %>% 
  dplyr::group_by(adm1name) %>% 
  dplyr::summarise(n = srvyr::survey_total(count), 
                   plsmdn = srvyr::survey_total(pv18s), 
                   plsmdprev = srvyr::survey_mean(pv18s, vartype = c("se", "ci"), level = 0.95)) %>% 
  dplyr::left_join(., DRCprov)


pvprov.weighted <- sf::st_as_sf(pvprov.weighted)
sf::st_crs(pvprov.weighted) <-  sf::st_crs(ge)
# need ints (binomail prob), so will round
pvprov.weighted <- pvprov.weighted %>% 
  dplyr::mutate(plsmdn = round(plsmdn, 0),
                n = round(n, 0))

pvprov.weighted.nosf <- pvprov.weighted
sf::st_geometry(pvprov.weighted.nosf) <- NULL


```


#### Diagnostic Chains
Run out four diagnostic chains to check convergence. 
```{r}
#..............................................................
# read in diagnostic chains
#..............................................................
mod.framework <- readRDS("~/Documents/GitHub/VivID_Epi/analyses/07-spatial_prediction/ProvModels/ProvModel_diag_chains.RDS")
```
#### MCMC Diagnostics 
Note, our goal is to have the effective sample sizes (`n.effective`) to be at least 500 for all parameters. In addition, we will visually check for convergence among the four chains. 

##### Param Diagnostics
```{r}
#-------------------------------------------------------------------------
# MCMC Diagnostics
#-------------------------------------------------------------------------
mod.framework$mcmc.modsum <- purrr::map(mod.framework$MCMC, print) # note, print is overloaded here
# CI mean, mode, median
mod.framework$summresults <- purrr::map(mod.framework$mcmc.modsum, "summary.results")
# get samples for HPD
mod.framework$samples <- purrr::map(mod.framework$MCMC, "samples")
# get HPD
mod.framework$HPD <- purrr::map(mod.framework$samples, HDInterval::hdi, credMass = 0.95)
# subset HPD to relevant params
mod.framework$HPD.summ <- purrr::map(mod.framework$HPD, 
                                     function(x){
                                       ret <- x[ names(x) %in% c("beta", "rho", "tau2") ]
                                       ret <- lapply(ret, function(y){
                                         ret <- t(y)
                                         colnames(ret) <- c("HPD 0.025", "HPD 0.975")
                                         return(ret) }) %>% 
                                         do.call("rbind.data.frame", .)
                                     })

mod.framework$summresults <- purrr::pmap(mod.framework[,c("summresults", "HPD.summ")], 
                                         function(summresults, HPD.summ){
                                           pars <- rownames(summresults)
                                           ret <- cbind.data.frame(pars = pars,
                                                                   cbind( summresults, HPD.summ))
                                           return(ret)
                                         })

```

###### Summary Stats
```{r, results='asis'}
mod.framework %>% 
  dplyr::select(c("name", "formula", "summresults")) %>% 
  tidyr::unnest(cols = "summresults") %>% 
    DT::datatable(., 
                rownames = F,
                options = list(
                  searching = F,
                  pageLength = 5,
                  dom = 'Bfrtip', 
                  buttons = c('csv')))
```


##### Diagnostic Chains
Note, there are too many chains for visualizing here. Writing out to local directory. 
```{r}

#............................
# Let's Look at the Chains
#............................
mod.framework$betachains <- purrr::map(mod.framework$samples, "beta")
mod.framework$phichains <- purrr::map(mod.framework$samples, "phi")
mod.framework$tau2chains <- purrr::map(mod.framework$samples, "tau2")
mod.framework$rhochains <- purrr::map(mod.framework$samples, "rho")


chains <- mod.framework %>% 
  dplyr::select(c("name", "betachains", "phichains", "tau2chains", "rhochains")) %>% 
  dplyr::group_by(name) %>% 
  dplyr::mutate(chainnum = 1:dplyr::n())

mydiagnosticdir <- "analyses/07-spatial_prediction/prov_map_diagnostic_chains/"
dir.create(mydiagnosticdir, recursive = T)
pmap(.l = chains[,c("name", "chainnum", "betachains", "phichains", "tau2chains", "rhochains")],
     .f  = make_mcmc_chain_plots.carbayes,
     diag.dir = mydiagnosticdir)


```

## Final Long Chain
Now, we will run out one final long chain with 1e5 burnin iterations and 1e8 sampling iterations for each of our base models. 

```{r}
mod.framework.long <- readRDS("~/Documents/GitHub/VivID_Epi/analyses/07-spatial_prediction/ProvModels/ProvModel_long_chains.RDS")

```

#### Long Chain MCMC Diagnostics 
Note, our goal is still to have the effective sample sizes (`n.effective`) to be at least 500 for all parameters. In addition, we will visually check for convergence among the four chains. 

##### Long Chain Param Diagnostics

```{r}
#-------------------------------------------------------------------------
# MCMC Diagnostics
#-------------------------------------------------------------------------
mod.framework.long$mcmc.modsum <- purrr::map(mod.framework.long$MCMC, print) # note, print is overloaded here
mod.framework.long$summresults <- purrr::map(mod.framework.long$mcmc.modsum, "summary.results")
# get samples for HPD
mod.framework.long$samples <- purrr::map(mod.framework.long$MCMC, "samples")
# get HPD
mod.framework.long$HPD <- purrr::map(mod.framework.long$samples, HDInterval::hdi, credMass = 0.95)
# subset HPD to relevant params
mod.framework.long$HPD.summ <- purrr::map(mod.framework.long$HPD, 
                                     function(x){
                                       ret <- x[ names(x) %in% c("beta", "rho", "tau2") ]
                                       ret <- lapply(ret, function(y){
                                         ret <- t(y)
                                         colnames(ret) <- c("HPD 0.025", "HPD 0.975")
                                         return(ret) }) %>% 
                                         do.call("rbind.data.frame", .)
                                     })

mod.framework.long$summresultsdf <- purrr::pmap(mod.framework.long[,c("summresults", "HPD.summ")], 
                                         function(summresults, HPD.summ){
                                           pars <- rownames(summresults)
                                           ret <- cbind.data.frame(pars = pars,
                                                                   cbind( summresults, HPD.summ))
                                           return(ret)
                                         })


#..............................................................
# Means for comparison to median
#..............................................................
mod.framework.long$posteriormeans <- purrr::pmap(mod.framework.long[,c("samples", "summresults")], 
                                            function(samples, summresults){
  betas <- apply(samples$beta, 2, mean)
  names(betas) <- row.names(summresults)[!row.names(summresults) %in% c("tau2", "rho")]
  tau2 <-  apply(samples$tau2, 2, mean)
  names(tau2) <- "tau2"
  rho <- apply(samples$rho, 2, mean)
  names(rho) <- "rho"
  
  params <- matrix(NA, nrow = 1, ncol = length(c(betas, tau2, rho)))
  params <- c(betas, tau2, rho)
  params <- data.frame(covar = names(params), postmean = params)
  return(params)
})

#..............................................................
# also want to get phis here for each province
#..............................................................
mod.framework.long$posteriorphis <- purrr::map(mod.framework.long$samples, 
                                            function(smpl){
                                              
  phimean <- apply(smpl$phi, 2, mean)
  phimedian <- apply(smpl$phi, 2, median)
  phiperc025 <- apply(smpl$phi, 2, quantile, 0.025)
  phiperc975 <- apply(smpl$phi, 2, quantile, 0.975)
  
  phihpd <- HDInterval::hdi(smpl$phi, credMass = 0.95)
  
  # effective sampling
  phineff <- apply(smpl$phi, 2, coda::effectiveSize)
  
  # Geweke's Diagnostic
  phigwe <- apply(smpl$phi, 2, coda::geweke.diag)
  phigwe <- purrr::map_dbl(phigwe, "z")
  phi_gwepv <- purrr::map_dbl(phigwe, function(x) {2*pnorm(abs(x), lower.tail=FALSE)})
  
  phis <- list(phimean, phimedian, phiperc025, phiperc975, phihpd, 
               phineff, phigwe, phi_gwepv)
  phis <- do.call("rbind.data.frame", phis)
  # bind together
  phis <- cbind.data.frame(statistic = c("Mean", "Median", "Perc0.025", "Perc97.5",
                                         "HPD 0.025", "HPD 0.975", "Neff",
                                          "Geweke.diag", "Geweke.pval"),
                   phis)
                   
  # put names in 
  colnames(phis)[2:ncol(phis)] <- pvprov.weighted$adm1name
  return(phis)
  
})


mod.framework.long.res <- mod.framework.long %>% 
  dplyr::select(c("name", "formula", "summresultsdf")) %>% 
  tidyr::unnest(cols = "summresultsdf") %>% 
  dplyr::select("name", "formula", "pars", "n.sample", "Median", dplyr::starts_with("HPD"),
                "2.5%", "97.5%", "% accept",
                "n.effective", "Geweke.diag") %>% 
  dplyr::mutate(Geweke.pval = 2*pnorm(abs(Geweke.diag), lower.tail=FALSE))

```

###### Summary Stats, Percentiles
```{r, results='asis'}
mod.framework.long.res %>% 
    DT::datatable(., 
                rownames = F,
                options = list(
                  searching = F,
                  pageLength = 20,
                  dom = 'Bfrtip', 
                  buttons = c('csv')))
```

###### Summary Stats, Means
```{r, results='asis'}
mod.framework.long %>% 
  dplyr::select(c("name", "formula", "posteriormeans")) %>% 
  tidyr::unnest(cols = "posteriormeans") %>% 
    DT::datatable(., 
                rownames = F,
                options = list(
                  searching = F,
                  pageLength = 20,
                  dom = 'Bfrtip', 
                  buttons = c('csv')))
```

###### Summary Stats, Phis
```{r, results='asis'}
mod.framework.long %>% 
  dplyr::select(c("name", "formula", "posteriorphis")) %>% 
  dplyr::mutate(var = "phi") %>% 
  tidyr::unnest(cols = "posteriorphis") %>% 
    DT::datatable(., 
                rownames = F,
                options = list(
                  searching = F,
                  pageLength = 20,
                  dom = 'Bfrtip', 
                  buttons = c('csv')))
```



Note, still a lot of chains for visualizing here. Writing out to local directory. 
```{r}

#............................
# Let's Look at the final chain
#............................
mod.framework.long$samples <- purrr::map(mod.framework.long$MCMC, "samples")
mod.framework.long$betachains <- purrr::map(mod.framework.long$samples, "beta")
mod.framework.long$phichains <- purrr::map(mod.framework.long$samples, "phi")
mod.framework.long$tau2chains <- purrr::map(mod.framework.long$samples, "tau2")
mod.framework.long$rhochains <- purrr::map(mod.framework.long$samples, "rho")
mod.framework.long$fittedchains <- purrr::map(mod.framework.long$samples, "fitted")


chains <- mod.framework.long %>% 
  dplyr::select(c("name", "betachains", "phichains", "tau2chains", "rhochains", "fittedchains")) %>% 
  dplyr::group_by(name) %>% 
  dplyr::mutate(chainnum = 1:dplyr::n())


myfinalchain <- "~/Documents/GitHub/VivID_Epi/analyses/07-spatial_prediction/prov_map_final_long_chain/"
dir.create(myfinalchain, recursive = T)
dir.create(mydiagnosticdir, recursive = T)
pmap(.l = chains[,c("name", "chainnum", "betachains", "phichains", "tau2chains", "rhochains")],
     .f  = make_mcmc_chain_plots.carbayes,
     diag.dir = myfinalchain)


```


<!-- ### Long Chain DIC -->

<!-- ```{r} -->


<!-- mod.framework.long$modfit <- purrr::map(mod.framework.long$mcmc.modsum, "modelfit") -->

<!-- # note in order to be consistent, with the PrevMap approach, -->
<!-- # I want Gelman's DIC: DICg = mu + sigma -->
<!-- # can get this from the log likelihood provided by CarBayes.  -->

<!-- # CarBayes nicely outputs the Fitted Values, from which I can calculate a log-likelihood -->
<!-- dimnames(mod.framework.long$W[[1]])[[1]] -->

<!-- mod.framework.long$LL <- purrr::pmap(mod.framework.long[, c("data", "trials", "MCMC")],  -->
<!--   function(data, trials, MCMC){ -->
<!--   Yi <- data$plsmdn -->
<!--   ni <- trials -->
<!--   Ti <- MCMC$samples$fitted -->

<!--   LL <- c() -->
<!--   for(s in 1:nrow(Ti)){ # for every sim -->
<!--     LL.iter <- 0 -->
<!--     for(i in 1:ncol(Ti)){ # for every spatial unit -->
<!--       LL.iter <- dbinom(x = Yi[i], size = ni[i], prob = Ti[s, i]/ni[i], log = T) + LL.iter -->
<!--       LL.iter -->
<!--     } -->
<!--     LL <- append(LL.iter, LL) -->

<!--   } -->

<!--   LL <- return(LL) -->
<!-- }) -->


<!-- mod.framework.long$DICg <- purrr::map(mod.framework.long$LL, function(x){ -->
<!--   mu = mean(x) -->
<!--   sigma = var(x)/2 -->
<!--   DICg = mu + sigma -->
<!--   return(DICg) -->
<!-- }) -->


<!-- mod.framework.long$DICs <- purrr::map(mod.framework.long$modfit, "DIC") -->


<!-- ``` -->

<!-- ```{r, results='asis'} -->
<!-- data.frame(name = mod.framework.long$name, DICg = unlist(mod.framework.long$DICg), -->
<!--            DICs = unlist(mod.framework.long$DICs)) %>%  -->
<!--   DT::datatable(.,  -->
<!--                 rownames = F, -->
<!--                 options = list( -->
<!--                   searching = F, -->
<!--                   pageLength = 6, -->
<!--                   dom = 'Bfrtip',  -->
<!--                   buttons = c('csv'))) -->

<!-- ``` -->

```{r}

# save out this RDS file
saveRDS(mod.framework.long, 
        file = "~/Documents/GitHub/VivID_Epi/analyses/07-spatial_prediction/prov_map_final_long_chain/Province_Bayes_Hierarchial_Model_longchain.rds")

```
