---
output: html_document
editor_options: 
  chunk_output_type: console
---
# Bayesian Hierarchial Spatial Cluster Models 

```{r, include=FALSE}
knitr::opts_chunk$set(echo = T, warning = F, message = F, eval = T, results = 'hide',
                      fig.align = 'center', fig.width = 8, fig.height = 8)
```

```{r}

source("~/Documents/GitHub/VivID_Epi/R/00-functions_basic.R")
source("~/Documents/GitHub/VivID_Epi/R/00-functions_maps.R") 
source("~/Documents/GitHub/VivID_Epi/R/00-MCMC_diagnostics.R")
library(tidyverse)
library(sf)
library(srvyr) 
library(rgeos)
library(raster)
library(PrevMap)
set.seed(48)


#......................
# Import Data
#......................
dt <- readRDS("~/Documents/GitHub/VivID_Epi/data/derived_data/vividepi_recode_completecases.rds")
dtsrvy <- makecd2013survey(survey = dt)
mp <- readRDS("~/Documents/GitHub/VivID_Epi/data/derived_data/basic_cluster_mapping_data.rds")
ge <- readRDS(file = "~/Documents/GitHub/VivID_Epi/data/raw_data/dhsdata/VivIDge.RDS")
DRCprov <- readRDS("~/Documents/GitHub/VivID_Epi/data/map_bases/vivid_DRCprov.rds")

```

```{r}
#......................
# Subset to Pv
#......................
pvclust.weighted <- mp$data[mp$plsmdmspec == "pv18s" & mp$maplvl == "hv001"][[1]]
# vectors have destroyed spatial class, need to remake
pvclust.weighted <- sf::st_as_sf(pvclust.weighted)
sf::st_crs(pvclust.weighted) <-  sf::st_crs(ge)

# need to keep integers, so will round
pvclust.weighted <- pvclust.weighted %>% 
  dplyr::mutate(plsmdn = round(plsmdn, 0),
                n = round(n, 0))


```

```{r}

#-------------------------------------------------------------------------
# Aggregate Covariates
#-------------------------------------------------------------------------
# precipitation already in dataset 
pvclst.covar <- dt %>% 
  dplyr::select("hv001", "precip_mean_cont_scale_clst", "temp_mean_cont_scale_clst") %>% 
  dplyr::filter(!duplicated(.))

# bring in cropland
crop <- readRDS("data/derived_data/vividepi_cropland_propmeans.rds") %>% 
  dplyr::select(c("hv001", "cropprop_cont_scale_clst"))
# bring in nightlights
nightlists <- readRDS("data/derived_data/vividepi_night_clstmeans.rds") %>% 
  dplyr::select(c("hv001", "nightlightsmean_cont_scale_clst"))

pvclst.covar <- dplyr::left_join(x = pvclst.covar, y = crop, by = "hv001") %>% 
  dplyr::left_join(x = ., y = nightlists, by = "hv001")

# join together
pvclust.weighted <- dplyr::left_join(pvclust.weighted, pvclst.covar, by = "hv001")
pvclust.weighted.nosf <- pvclust.weighted
sf::st_geometry(pvclust.weighted.nosf) <- NULL

riskvars = c("precip_mean_cont_scale_clst", "temp_mean_cont_scale_clst", 
             "cropprop_cont_scale_clst", "nightlightsmean_cont_scale_clst")


```

## Spatial Autocorrelation EDA for Gaussian Processes
Note, using the vignette/resource provided by [Giorgi & Diggle 2017](https://www.jstatsoft.org/article/view/v078i08) and `rgeos`.


```{r}
uvec <- c(seq(0, 1, by = 0.2), seq(1, 10))
```

### Case Counts
```{r, results='asis'}

pvclust.weighted.geodata <- geoR::as.geodata(obj = pvclust.weighted.nosf,
                                             coords.col = c("longnum", "latnum"),
                                             data.col = "plsmdn",
                                             covar.col = riskvars)

plot(pvclust.weighted.geodata)

```


#### Case-Variogram

```{r, results='asis'}

pv.vario.counts <- geoR::variog(pvclust.weighted.geodata,
                                bin.cloud = T,
                                uvec = uvec)

par(mfrow = c(1,3))
points(pvclust.weighted.geodata, xlab = "Coord X", 
       ylab = "Coord Y",
       cex.max = 0.7, col = gray(seq(1, 0.1, l = 100)),
       pt.divide = "equal")
plot(pv.vario.counts)

plot(pv.vario.counts, bin.cloud = T)
mtext("Empirical Variogram for P.vivax Counts", side = 3,  line = -6, outer = TRUE)

graphics.off()

```

This does not indicate a great degree (if any) spatial structuring. The classic variogram should follow a log-curve and have a sill that is reached at some distance. Of note, the potential nugget effect here is huge.  


### Prevalence
N.B. I am using a empirical logit transformation here. However, in the Bayesian models, I am using an exact approach for the binomial counts. This is purely so we can model this as a normal process (and speed thnings up/use standard regression approachs for EDA).
```{r, results='asis'}
# transform count of "successes" to logit space
pvclust.weighted.nosf$plsmdlogit <- log( (pvclust.weighted.nosf$plsmdn + 0.5)/(pvclust.weighted.nosf$n - pvclust.weighted.nosf$plsmdn + 0.5) ) # 0.5 as tolerance for 0s

pvclust.weighted.geodata <- geoR::as.geodata(obj = pvclust.weighted.nosf,
                                             coords.col = c("longnum", "latnum"),
                                             data.col = "plsmdlogit",
                                             covar.col = riskvars)
plot(pvclust.weighted.geodata)


```




#### Prevelance-Variogram

```{r, results='asis'}

pv.vario.prev <- geoR::variog(pvclust.weighted.geodata,
                              bin.cloud = T,
                              uvec = uvec)

par(mfrow = c(1,3))
points(pvclust.weighted.geodata, xlab = "Coord X", 
       ylab = "Coord Y",
       cex.max = 0.7, col = gray(seq(1, 0.1, l = 100)),
       pt.divide = "equal")
plot(pv.vario.prev)

plot(pv.vario.prev, bin.cloud = T)

mtext("Empirical Variogram for P.vivax Prevelance", side = 3,  line = -6, outer = TRUE)

graphics.off()

```
A remarkable lack of spatial structure...

#### Estimation of Variogram Parameters
I.e. nugget effect, sill, and range. Will test a Matern and Exponential Covariance and compare. 
```{r}

#..........................
# Maximum Likelihood
#..........................
ml.exp <- likfit(pvclust.weighted.geodata, 
                 ini = c(1, 0.5),
                 cov.model = "exp",
                 fix.nugget = F, 
                 nugget = 0,
                 fix.kappa = F)

ml.matern <- likfit(pvclust.weighted.geodata, 
                    ini = c(1, 0.5),
                    cov.model = "matern",
                    fix.nugget = F, 
                    nugget = 0,
                    fix.kappa = F)

#..........................
# OLS
#..........................

ols.exp <- variofit(pv.vario.prev, 
                    ini = c(1, 0.5),
                    cov.model = "exp",
                    fix.nugget = F, 
                    nugget = 0,
                    fix.kappa = F) 

ols.matern <- variofit(pv.vario.prev, 
                       ini = c(1, 0.5),
                       cov.model = "matern",
                       fix.nugget = F, 
                       nugget = 0,
                       fix.kappa = F)



par(mfrow = c(1, 2))
plot(pv.vario.prev, main = "Maximum Likelihood Estimation")
lines(ml.exp, max.dist = 20, lty = 1, lwd = 2)
lines(ml.matern, max.dist = 20, lty = 2, lwd = 2, col = "red")
legend(2, 4, legend = c("Exp", "Matern"), 
       lty = c(1, 2), col = c("black", "red"), cex = 0.7)

plot(pv.vario.prev, main = "Ordinary Least Square")
lines(ols.exp, max.dist = 20, lty = 1, lwd = 2)
lines(ols.matern, max.dist = 20, lty = 2, lwd = 2, col = "red")
legend(2, 4, legend = c("Exp", "Matern"), 
       lty = c(1, 2), col = c("black", "red"), cex = 0.7)

graphics.off()

```
Truly impressive lack of spatial structure. From models above, an appropriate _kappa_ value fro the Matern covariance matrix appeared to be 0.5 or 1. Let's explore that specifically below.

#### Matern Shape
```{r}
#......................
# Matern Shape, K
#......................

# look at kappa smooth parameter for matern covariance
profile.kappa <- invisible( PrevMap::shape.matern(plsmdlogit ~ 1,
                                                  coords = ~ longnum + latnum,
                                                  data = pvclust.weighted.nosf,
                                                  set.kappa = seq(0.1, 10, length = 16),
                                                  start.par = c(0.2, 0.05), # starting values for the scale parameter phi and the relative variance of the nugget effect nu2
                                                  coverage = NULL # CI coverage
) )



```

```{r, results='asis'}

plot(profile.kappa)

```
The max _kappa_ value was found to be `r profile.kappa$set.kappa[ which(profile.kappa$val.kappa == max(profile.kappa$val.kappa)) ]`. Will set it to 1.5 (fixed now in subsequent analyses).



## Hierarchial Bayesian Spatial Models for Cluster Prevalence 

### Model Framework 
NB, here it is not quite the same to "turn off space". Instead, we will let the covariance matrix be considered as a continuous process and let $\sigma^2$ and Matern correlation, $\phi$ vary under the model (we fixed $\kappa$). 

#### Priors & Sampling
(Please open up code for inquiries).



### Diagnostic Chains
Run out four diagnostic chains to check convergence. 
```{r}

mod.framework <- readRDS("~/Documents/GitHub/VivID_Epi/analyses/07-spatial_prediction/_rslurm_prevmap_diagnostic_chains/params.RDS")

mcmc.ret <- list.files(path = "~/Documents/GitHub/VivID_Epi/analyses/07-spatial_prediction/_rslurm_prevmap_diagnostic_chains/", full.names = T, pattern = ".RDS")
mcmc.ret <- mcmc.ret[!grepl("params|f.", mcmc.ret)]

# 0-7 index here so don't have to worry about char 10 and 1 being next to eachother

mod.framework$mcmc <- purrr::map(mcmc.ret, function(x){return(readRDS(x)[[1]])})

```


#### MCMC Diagnostics Chains
Note, our goal is to have the effective sample sizes (`n.effective`) to be at least 1,000 for all parameters. In addition, we will visually check for convergence among the four chains. 

```{r}
mod.framework$summresults <- purrr::map(mod.framework$mcmc, summary, hpd.coverage = 0.95)
mod.framework$summdiagret <- purrr::map(mod.framework$mcmc, get_diag_summ_results.Bayes.PrevMap)


mod.framework$paramtable <- purrr::map(mod.framework$summdiagret, "summresults")
mod.framework$traceplots <- purrr::map(mod.framework$summdiagret, "traceplots")
mod.framework$autocorrplot <- purrr::map(mod.framework$summdiagret, "autocorrplots")

```

##### Param Diagnostics for Diagnostic Runs
```{r, results='asis'}

mod.framework %>% 
  dplyr::select(c("name", "formula", "paramtable")) %>% 
  tidyr::unnest(cols="paramtable") %>% 
  kableExtra::kable(format = "html", escape = F) %>%
  kableExtra::kable_styling("striped", full_width = F) 


```



##### MCMC Trace Plots for Diagnostic Runs
Too many plots again to visualize here, so will send out locally.
```{r}
diagchain <- "~/Documents/GitHub/VivID_Epi/analyses/07-spatial_prediction/cluster_gaus_diagnostic_chain/"
dir.create(diagchain, recursive = T)

for(i in 1:nrow(mod.framework)){
  fileout <- paste0(diagchain, "/", mod.framework$name[i], "_diagnostic_chains_TRACEPLOTS_", i, ".pdf")
  pdf(fileout)
  invisible(lapply(mod.framework$traceplots[i], print)) 
  dev.off()
}


for(i in 1:nrow(mod.framework)){
  fileout <- paste0(diagchain, "/", mod.framework$name[i], "_diagnostic_chains_AUTOPLOTS_", i, ".pdf")
  pdf(fileout)
  invisible(lapply(mod.framework$autocorrplot[i], print)) 
  dev.off()
}

```


## Long Chain
```{r}

long.intercept <- readRDS("~/Documents/GitHub/VivID_Epi/analyses/07-spatial_prediction/prevmap_long_chains/longrun-prevmapbayes-intercept.rds")
long.covar <- readRDS("~/Documents/GitHub/VivID_Epi/analyses/07-spatial_prediction/prevmap_long_chains/longrun-prevmapbayes-mod.rds")
long.framework <- tibble::tibble(name = c("intercept", "covars"),
                                 mcmc = list(long.intercept, long.covar))

```

### Final Params
```{r}

long.framework$summresults <- purrr::map(long.framework$mcmc, summary, hpd.coverage = 0.95)
long.framework$summdiagret <- invisible( purrr::map(long.framework$mcmc, get_diag_summ_results.Bayes.PrevMap) )


long.framework$paramtable <- purrr::map(long.framework$summdiagret, "summresults")

long.frameworks.summresults <- long.framework %>% 
  dplyr::select(c("name", "paramtable")) %>% 
  tidyr::unnest(cols="paramtable") 
```

```{r, results='asis'}
long.frameworks.summresults %>% 
  kableExtra::kable(format = "html", escape = F) %>%
  kableExtra::kable_styling("striped", full_width = F) 



```

### Final Diag Plots
#### Intercept Only Diagnostics 
```{r, results='asis'}
PrevMap::trace.plot(long.intercept, param = "beta", component.beta = 1)
PrevMap::autocor.plot(long.intercept, param = "beta", component.beta = 1)

PrevMap::trace.plot(long.intercept, param = "tau2")
PrevMap::autocor.plot(long.intercept, param = "tau2")

PrevMap::trace.plot(long.intercept, param = "sigma2")
PrevMap::autocor.plot(long.intercept, param = "sigma2")

PrevMap::trace.plot(long.intercept, param = "phi")
PrevMap::autocor.plot(long.intercept, param = "phi")

```

#### Covariate Model Diagnostics 
```{r, results='asis'}
PrevMap::trace.plot(long.covar, param = "beta", component.beta = 1)
PrevMap::autocor.plot(long.covar, param = "beta", component.beta = 1)


PrevMap::trace.plot(long.covar, param = "beta", component.beta = 2)
PrevMap::autocor.plot(long.covar, param = "beta", component.beta = 2)

PrevMap::trace.plot(long.covar, param = "tau2")
PrevMap::autocor.plot(long.covar, param = "tau2")

PrevMap::trace.plot(long.covar, param = "sigma2")
PrevMap::autocor.plot(long.covar, param = "sigma2")

PrevMap::trace.plot(long.covar, param = "phi")
PrevMap::autocor.plot(long.covar, param = "phi")


```


## DIC of Final Models
```{r}

# note because the model returns the S matrix which is the posterior for the random effect
# and it returns the posterior betas, we can calculate the Ti from each model 
# from there, it is straightforward to calculate the likelihood as a series of 
# independently drawn binomial trials

long.framework$randomeff <- purrr::map(long.framework$mcmc, "S")
long.framework$betas <- purrr::map(long.framework$mcmc, "estimate")
long.framework$betas <- purrr::map(long.framework$betas, function(x){return(x[, colnames(x)[!colnames(x) %in% c("sigma^2", "phi", "tau^2")] ] )})
long.framework$X <- purrr::map(long.framework$mcmc, "D") # matrix of covariates
long.framework$Yi <- lapply(1:nrow(long.framework), function(x) return(pvclust.weighted$plsmdn)) # binomial successes
long.framework$ni <- lapply(1:nrow(long.framework), function(x) return(pvclust.weighted$n)) # observations 

long.framework$Ti <- purrr::pmap(long.framework[,c("X", "betas", "randomeff")], 
                                 function(X, betas, randomeff){
                                   bi <- X %*% t(betas) # get the X (nxp matrix) * the betas (pxsim matrix)
                                   Ti <- randomeff + t(bi) # random effects is in sim x n so tranpose bi to match it
                                   return(Ti)
                                 })

long.framework$LL <- purrr::pmap(long.framework[,c("Yi", "ni", "Ti")], function(Yi, ni, Ti){
  LL <- c()
  for(s in 1:nrow(Ti)){ # for every sim
    LL.iter <- 0
    for(i in 1:ncol(Ti)){ # for every spatial unit
      LL.iter <- dbinom(x = Yi[i], size = ni[i], prob = expit(Ti[s, i]), log = T) + LL.iter
      LL.iter
    }
    LL <- append(LL.iter, LL)
    
  }
  
  LL <- return(LL)
})


long.framework$DICg <- purrr::map(long.framework$LL, function(x){
  mu = mean(x)
  sigma = var(x)/2
  DICg = mu + sigma
  return(DICg)
})


```

```{r, results = 'asis'}

long.framework %>% 
  dplyr::select(c("name", "DICg")) %>% 
  tidyr::unnest(cols="DICg") %>% 
  magrittr::set_colnames(c("Model", "DICg")) %>% 
  kableExtra::kable(format = "html", escape = F) %>%
  kableExtra::kable_styling("striped", full_width = F) 


```

### Log Likelihood Trace Plots for Final Models
```{r, results = 'asis'}

plot(long.framework$LL[[1]], main = "Intercept Model", type = "l")
plot(long.framework$LL[[2]], main = "Covars Model", type = "l")

```
