---
title: "Bayesian Hierarchial Spatial Cluster Models for _P. vivax_ among Asymptomatic Adults in the DRC"
author: "Nicholas F. Brazeau"
date: "`r format(Sys.time(), '%B %d, %Y')`"
output: 
  html_document:
    highlight: textmate
    theme: lumen
    toc: yes
    code_folding: hide
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = F, warning = F, message = F, eval = T, results = 'hide',
                      fig.align = 'center', fig.width = 8, fig.height = 8)
Sys.setenv(RSTUDIO_PANDOC="/usr/local/Cellar/pandoc/2.7.3/bin/")
Sys.setenv('R_MAX_VSIZE'=100000000000)

```


```{r}
setwd("~/Documents/GitHub/VivID_Epi/")
source("~/Documents/GitHub/VivID_Epi/R/00-functions_basic.R")
source("~/Documents/GitHub/VivID_Epi/R/00-functions_maps.R") 
library(tidyverse)
library(sf)
library(srvyr) 
library(rgeos)
library(rgdal)
library(geoR)
library(raster)
library(PrevMap)
set.seed(48)
tol <- 1e-3
#......................
# Import Data
#......................
dt <- readRDS("data/derived_data/vividepi_recode.rds")
dtsrvy <- makecd2013survey(survey = dt)
mp <- readRDS("data/derived_data/basic_cluster_mapping_data.rds")
ge <- sf::st_as_sf( readRDS("data/raw_data/dhsdata/datasets/CDGE61FL.rds") )
DRCprov <- readRDS("data/map_bases/vivid_DRCprov.rds")

```

```{r}
#......................
# Subset to Pv
#......................
pvclust.weighted <- mp$data[mp$plsmdmspec == "pv18s" & mp$maplvl == "hv001"][[1]]
# vectors have destroyed spatial class, need to remake
pvclust.weighted <- sf::st_as_sf(pvclust.weighted)
sf::st_crs(pvclust.weighted) <-  sf::st_crs(ge)

# need to keep integers, so will round
pvclust.weighted <- pvclust.weighted %>% 
  dplyr::mutate(plsmdn = round(plsmdn, 0),
                n = round(n, 0))


```

```{r}

#-------------------------------------------------------------------------
# Aggregate Covariates
#-------------------------------------------------------------------------

pvclst.covar <- dtsrvy %>% 
  dplyr::group_by(hv001) %>% 
  dplyr::summarise(precip_mean_cont_scale_clst = srvyr::survey_mean(precip_mean_cont_scale_clst, na.rm = T, vartype = c("se", "ci"), level = 0.95) # identical by clst but ok
  )

pvclust.weighted <- dplyr::left_join(pvclust.weighted, pvclst.covar, by = "hv001")
pvclust.weighted.nosf <- pvclust.weighted
sf::st_geometry(pvclust.weighted.nosf) <- NULL

```

## Spatial Autocorrelation EDA for Gaussian Processes
Note, using resourced from [Giorgi & Diggle 2017](https://www.jstatsoft.org/article/view/v078i08) and `rgeos`.


```{r}
riskvars = c("precip_mean_cont_scale_clst")
uvec <- c(seq(0, 1, by = 0.2), seq(1, 10))
```

### Case Counts
```{r, results='asis'}

pvclust.weighted.geodata <- geoR::as.geodata(obj = pvclust.weighted.nosf,
                                             coords.col = c("longnum", "latnum"),
                                             data.col = "plsmdn",
                                             covar.col = riskvars)

plot(pvclust.weighted.geodata)

```


#### Case-Variogram

```{r, results='asis'}

pv.vario.counts <- geoR::variog(pvclust.weighted.geodata,
                                bin.cloud = T,
                                uvec = uvec)

par(mfrow = c(1,3))
points(pvclust.weighted.geodata, xlab = "Coord X", 
       ylab = "Coord Y",
       cex.max = 0.7, col = gray(seq(1, 0.1, l = 100)),
       pt.divide = "equal")
plot(pv.vario.counts)

plot(pv.vario.counts, bin.cloud = T)
mtext("Empirical Variogram for P.vivax Counts", side = 3,  line = -6, outer = TRUE)

graphics.off()

```

This does not indicate a great degree (if any) spatial structuring. The classic variogram should follow a log-curve and have a sill that is reach at some distance. Of note, the potential nugget effect here is huge.  


### Prevalence
```{r, results='asis'}
# transform count of "successes" to logit space
pvclust.weighted.nosf$plsmdlogit <- log( (pvclust.weighted.nosf$plsmdn + 0.5)/(pvclust.weighted.nosf$n - pvclust.weighted.nosf$plsmdn + 0.5) ) # 0.5 as tolerance for 0s

pvclust.weighted.geodata <- geoR::as.geodata(obj = pvclust.weighted.nosf,
                                             coords.col = c("longnum", "latnum"),
                                             data.col = "plsmdlogit",
                                             covar.col = riskvars)
plot(pvclust.weighted.geodata)


```




#### Prevelance-Variogram

```{r, results='asis'}

pv.vario.prev <- geoR::variog(pvclust.weighted.geodata,
                              bin.cloud = T,
                              uvec = uvec)

par(mfrow = c(1,3))
points(pvclust.weighted.geodata, xlab = "Coord X", 
       ylab = "Coord Y",
       cex.max = 0.7, col = gray(seq(1, 0.1, l = 100)),
       pt.divide = "equal")
plot(pv.vario.prev)

plot(pv.vario.prev, bin.cloud = T)

mtext("Empirical Variogram for P.vivax Prevelance", side = 3,  line = -6, outer = TRUE)

graphics.off()

```
A remarkable lack of spatial structure...

#### Estimation of Variogram Parameters
I.e. nugget effect, sill, and range. Will test a Matern and Exponential Covariance and compare. 
```{r}

#..........................
# Maximum Likelihood
#..........................
ml.exp <- likfit(pvclust.weighted.geodata, 
                 ini = c(1, 0.5),
                 cov.model = "exp",
                 fix.nugget = F, 
                 nugget = 0,
                 fix.kappa = F)

ml.matern <- likfit(pvclust.weighted.geodata, 
                    ini = c(1, 0.5),
                    cov.model = "matern",
                    fix.nugget = F, 
                    nugget = 0,
                    fix.kappa = F)

#..........................
# OLS
#..........................

ols.exp <- variofit(pv.vario.prev, 
                    ini = c(1, 0.5),
                    cov.model = "exp",
                    fix.nugget = F, 
                    nugget = 0,
                    fix.kappa = F) 

ols.matern <- variofit(pv.vario.prev, 
                       ini = c(1, 0.5),
                       cov.model = "matern",
                       fix.nugget = F, 
                       nugget = 0,
                       fix.kappa = F)



par(mfrow = c(1, 2))
plot(pv.vario.prev, main = "Maximum Likelihood Estimation")
lines(ml.exp, max.dist = 20, lty = 1, lwd = 2)
lines(ml.matern, max.dist = 20, lty = 2, lwd = 2, col = "red")
legend(2, 4, legend = c("Exp", "Matern"), 
       lty = c(1, 2), col = c("black", "red"), cex = 0.7)

plot(pv.vario.prev, main = "Ordinary Least Square")
lines(ols.exp, max.dist = 20, lty = 1, lwd = 2)
lines(ols.matern, max.dist = 20, lty = 2, lwd = 2, col = "red")
legend(2, 4, legend = c("Exp", "Matern"), 
       lty = c(1, 2), col = c("black", "red"), cex = 0.7)

graphics.off()

```
Truly impressive lack of spatial structure. From models above, an appropriate _kappa_ value fro the Matern covariance matrix appeared to be 0.5 or 1. Let's explore that specifically below.

#### Matern Shape
```{r, results='asis'}
#......................
# Matern Shape, K
#......................

# look at kappa smooth parameter for matern covariance
profile.kappa <- PrevMap::shape.matern(plsmdlogit ~ 1,
                                       coords = ~ longnum + latnum,
                                       data = pvclust.weighted.nosf,
                                       set.kappa = seq(0.1, 10, length = 16),
                                       start.par = c(0.2, 0.05), # starting values for the scale parameter phi and the relative variance of the nugget effect nu2
                                       coverage = NULL # CI coverage
                                      )



```
The max _kappa_ value was found to be `r profile.kappa$set.kappa[ which(profile.kappa$val.kappa == max(profile.kappa$val.kappa)) ]`. Will set it to 1.5 (fixed now in subsequent analyses).






## Hierarchial Bayesian Spatial Models for Cluster Prevalence 
### Model Framework 
NB, here it is not quite the same to "turn off space". Instead, we will let the covariance matrix be considered as a continuous process and let $\sigma^2$ and Matern correlation, $\phi$ vary under the model (we fixed $\kappa$). 
#### Priors & Sampling
(Please open up code for inquiries).



#### Diagnostic Chains
Run out four diagnostic chains to check convergence. 
```{r}

# READRDS  
  


```


#### MCMC Diagnostics 
Note, our goal is to have the effective sample sizes (`n.effective`) to be at least 1,000 for all parameters. In addition, we will visually check for convergence among the four chains. 

##### Param Diagnostics

##### MCMC Trace Plots
#TODO can overload coda here
```{r}
coda::effectiveSize(coda::mcmc(mod.framework$mcmc[[1]]$estimate[,1]))

mod.framework$coda <- purrr::map(mod.framework$mcmc, coda::mcmc)
mod.framework$neff <-  purrr::map(mod.framework$coda, coda::effectiveSize)

fit.Bayes = mod.framework$mcmc[[1]]

summary(fit.Bayes, hpd.coverage = 0.95)


par(mfrow=c(2,4))
autocor.plot(fit.Bayes,param="S",component.S="all")
autocor.plot(fit.Bayes,param="beta",component.beta=1)
autocor.plot(fit.Bayes,param="sigma2")
autocor.plot(fit.Bayes,param="phi")
trace.plot(fit.Bayes,param="S",component.S=30)
trace.plot(fit.Bayes,param="beta",component.beta=1)
trace.plot(fit.Bayes,param="sigma2")
trace.plot(fit.Bayes,param="phi")
```


## Long Chain
```{r}



```





