---
title: "IPTW Risk Factor Prevalence Ratios"
author: "Nicholas F. Brazeau"
date: "`r format(Sys.time(), '%B %d, %Y')`"
output: 
  html_document:
    highlight: textmate
    theme: lumen
    toc: yes
    code_folding: hide
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = T, warning = F, message = F, eval = T, results = 'hide')
```

```{r}
library(tidyverse)
remotes::install_github("malcolmbarrett/ggdag"); library(ggdag)
source("~/Documents/GitHub/VivID_Epi/R/00-functions_epi.R")
```


## DAG
Note, the canonical set is all nodes in the DAG that are not on the casual pathway (i.e. "mediators"). By including the canonical set, we have taken a conservative approach for controlling for "lingering" or "unmeasured" confounders. 
  
```{r, results='asis', fig.align='center', fig.width=8, fig.height=6}
vividdag <- dagitty::downloadGraph(x = "dagitty.net/mjKNQhB")
tidy_dag <- tidy_dagitty(vividdag)
DAGplot <- ggdag(tidy_dag) +
  theme_dag()

dagplot <- tidy_dag %>% 
  ggplot(aes(x = x, y = y, xend = xend, yend = yend, color = name)) +
  geom_dag_point() +
  geom_dag_edges() +
  geom_dag_text(color = "#ef3b2c", size = 2) +
  theme_dag() +
  scale_color_viridis_d() + 
  theme(legend.position = "none")



plot(dagplot)

jpeg(filename = "~/Documents/GitHub/VivID_Epi/results/figures/dag.jpg",
     width = 11, height = 8, units = "in", res=500)
plot(dagplot)
graphics.off()



```

```{r}
# import data
varstoinclude <- c("pv18s" , "pfldh", "hv001", "hv023", "hv005_wi", txs$target,
                   "hab1_cont_scale", "hv104_fctb", # need to add in covariates that don't have confounding ancestors but are needed elsewhere
                   "urban_rura_fctb", "alt_dem_cont_scale_clst",
                   "hiv03_fctb", # no longer considered risk factor bc too few observations
                   "longnum", "latnum")

dt <- readRDS("data/derived_data/vividepi_recode.rds")
sf::st_geometry(dt) <- NULL

# subset to complete cases
dt.ml.cc <- dt  %>% 
  dplyr::select(varstoinclude) %>% 
  dplyr::filter(complete.cases(.)) 


dcdr <- readxl::read_excel(path = "model_datamaps/sub_DECODER_covariate_map_v3.xlsx", sheet = 1) %>% 
  dplyr::mutate(risk_factor_raw = ifelse(is.na(risk_factor_raw), "n", risk_factor_raw),
                risk_factor_model = ifelse(is.na(risk_factor_model), "n", risk_factor_model)) %>% 
  dplyr::select(c("column_name", "abridged_var_label", "risk_factor_model", "level")) %>% 
  dplyr::filter(risk_factor_model == "y") %>% 
  dplyr::filter(column_name != "hiv03_fctb")

```

```{r}
# weights

params$SLpreds <-purrr::map(params$SL, "SL.predictions")
params$iptw <- purrr::pmap(params[,c("task", "SLpreds")], get_iptw_prob)
params$target <- unlist( purrr::map(params$task, mlr::getTaskTargetNames) )

wi <- params %>% 
  dplyr::select(c("target", "iptw"))


```

```{r}

makeiptwsrvy <- function(x){
  if(is.null(x)){
    x <- 1
  }
  dt.ml.cc$wi <- x*dt.ml.cc$hv005_wi
  dtsrvy <- dt.ml.cc %>% srvyr::as_survey_design(ids = hv001, 
                                              #   strata = hv023, 
                                                 weights = wi)
  return(dtsrvy)
    }


fitglmlogit <- function(outcome, target, iptwsrvy){
    iptwsrvy <- iptwsrvy %>% 
    dplyr::select(c(outcome, target))
  
  eq <- as.formula(paste0(outcome, "~", target))
  ret <- survey::svyglm(eq,
                        design = iptwsrvy,
                        family = quasibinomial(link="logit"))
  return(ret)
}

```


## _P. vivax_ Risk Factor IPTW-Prevelance Ratios
```{r}
#.......................
# Pvivax 
#.......................
pvivrskfctr <- dcdr$column_name[dcdr$risk_factor_model == "y"]
pvivrskfctr_models <- data.frame(outcome = rep("pv18s", length(pvivrskfctr)), 
                                 target = pvivrskfctr, stringsAsFactors=FALSE)

pvivrskfctr_models <- dplyr::left_join(pvivrskfctr_models, wi, by = "target")


pvivrskfctr_models$iptwsrvy <- purrr::map(pvivrskfctr_models$iptw, makeiptwsrvy)


pvivrskfctr_models$glmlogit <- purrr::pmap(pvivrskfctr_models[,c("outcome", "target", "iptwsrvy")], fitglmlogit)

pvivrskfctr_models$glmlogit_tidy <- purrr::map(pvivrskfctr_models$glmlogit,
                                               .f=function(x){
                                                 broom::tidy(x, exponentiate=TRUE, conf.int=TRUE)}
)

pvivrskfctr_est <- pvivrskfctr_models$glmlogit_tidy %>% 
  bind_rows() %>% filter(term != "(Intercept)") %>% 
  mutate_if(is.numeric, round, 2) %>% 
  mutate(species = "Pv")

```

## _P. falciparum_ IPTW-OR
```{r, results='asis'}
knitr::kable(pvivrskfctr_est)
```

## _P. falciparum_ Risk Factor IPTW-Prevelance Ratios
```{r}
#.......................
# Pfalciparum 
#.......................
# TODO update to include pf and pv as risk factors as well

pfalrskfctr <- dcdr$column_name[dcdr$risk_factor_model == "y" & dcdr$column_name != "pfldh_fctb"]
pfalrskfctr_models <- data.frame(outcome = rep("pfldh", length(pfalrskfctr)), 
                                 target = pfalrskfctr, stringsAsFactors=FALSE)

pfalrskfctr_models <- dplyr::left_join(pfalrskfctr_models, wi, by = "target")

pfalrskfctr_models$iptwsrvy <- purrr::map(pfalrskfctr_models$iptw, makeiptwsrvy)

pfalrskfctr_models$glmlogit <- purrr::pmap(pfalrskfctr_models[,c("outcome", "target", "iptwsrvy")], fitglmlogit)

pfalrskfctr_models$glmlogit_tidy <- purrr::map(pfalrskfctr_models$glmlogit,
                                               .f=function(x){
                                                 broom::tidy(x, exponentiate=TRUE, conf.int=TRUE)}
)

pfalrskfctr_est <- pfalrskfctr_models$glmlogit_tidy %>% 
  bind_rows() %>% filter(term != "(Intercept)") %>% 
  mutate_if(is.numeric, round, 2) %>% 
  mutate(species = "Pf")

```

## _P. falciparum_ IPTW-OR
```{r, results='asis'}
knitr::kable(pfalrskfctr_est)
```

## IPTW OR Plot
```{r, results='asis'}

#...................................................
# Tidy
#...................................................
pvriskest <- pvivrskfctr_models$glmlogit_tidy %>% 
  bind_rows() %>% filter(term != "(Intercept)") %>% 
  mutate_if(is.numeric, round, 2) %>% 
  dplyr::rename(column_name = term) %>% 
  dplyr::mutate(
    column_name = ifelse(grepl("_fctb", column_name),
                         stringr::str_extract(column_name, "[ -~]+_fctb"),
                         column_name)
  )

pvriskest <- dplyr::left_join(pvriskest, dcdr, by = "column_name") %>% 
  dplyr::mutate(species = "Pv")
orderrf <- pvriskest %>% 
  dplyr::arrange(level) %>% 
  dplyr::select(abridged_var_label) %>% 
  unlist(.)

# PF
pfriskest <- pfalrskfctr_models$glmlogit_tidy %>% 
  bind_rows() %>% filter(term != "(Intercept)") %>% 
  mutate_if(is.numeric, round, 2) %>% 
  dplyr::rename(column_name = term) %>% 
  dplyr::mutate(
    column_name = ifelse(grepl("_fctb", column_name),
                         stringr::str_extract(column_name, "[ -~]+_fctb"),
                         column_name)
  )

pfriskest <- dplyr::left_join(pfriskest, dcdr, by = "column_name") %>% 
  dplyr::mutate(species = "Pf")
malriskest <- dplyr::bind_rows(pvriskest, pfriskest)



#...................................................
# Make Plots
#...................................................

mal_iptw_plot <- malriskest %>% 
  dplyr::mutate(abridged_var_label = factor(abridged_var_label, levels = orderrf, ordered = T)) %>% 
  ggplot() +
  geom_hline(yintercept = 1, color = "#cb181d", linetype = "dashed") +
  geom_pointrange(aes(x = abridged_var_label, y = estimate, 
                      ymin = conf.low, ymax = conf.high,
                      color = factor(species)), alpha = 0.8, size = 1.5) +
  scale_color_viridis_d("Species") +
  coord_flip() + 
  ylab("Prevalence Odds Ratio") + 
  theme(
    plot.title =  element_text(family = "Helvetica", face = "bold", vjust = 0.5, hjust = 0.5, size = 14),
    axis.title.x = element_text(family = "Helvetica", face = "bold", vjust = 0.5, hjust = 0.5, size = 16),
    axis.text = element_text(family = "Helvetica", vjust = 0.5, hjust = 0.5, size = 14),
    axis.title.y = element_blank(),
    legend.title = element_text(family = "Helvetica", face = "bold", vjust = 0.5, hjust = 0.5, size = 16),
    legend.text = element_text(family = "Helvetica", vjust = 0.5, hjust = 0.5, size = 14, angle = 0),
    legend.position = "right",
    axis.line.x = element_line(color = "black", size = 1.5),
    axis.line.y = element_blank(),
    axis.ticks.y = element_blank(),
    panel.background = element_rect(fill = "transparent"),
    plot.background = element_rect(fill = "transparent"),
    panel.grid = element_blank(),
    panel.border = element_blank())
    


jpeg("~/Desktop/IPTW-figure-for-jon.jpg", height = 11, width = 8, units = "in", res = 500)
plot(mal_iptw_plot)
graphics.off()

```

