---
output: html_document
editor_options: 
  chunk_output_type: console
---
# Non-Parameteric Risk Factors

```{r, include=FALSE}
knitr::opts_chunk$set(echo = T, warning = F, message = F, eval = T, results = 'hide',
                      fig.align = 'center')
knitr::opts_knit$set(root.dir = here::here())

```
```{r}
set.seed(48)
remotes::install_github("nickbrazeau/icer")
library(icer)
library(tidyverse)
source("R/00-functions_basic.R")
source("R/00-functions_maps.R") 
library(tidyverse)
library(sf)
library(geosphere)
library(spdep)
library(raster)
library(srvyr) #wrap the survey package in dplyr syntax
library(RColorBrewer)

```


## Pf-Pv Interference
### Infection Composition Model Indepdent Model for Interference 
```{r}

surv.mle <- readRDS("analyses/08-nonparam_riskfacts/perm_rets/icer_model.rds")
coinfxnplotObj <- surv.mle$coinfxnplot$plot +
  theme(axis.text.x = element_text(angle = 90))

jpeg("results/figures/PvPfInterference.jpg",
     height = 8, width = 8, units = "in", res = 500)
plot(coinfxnplotObj)
graphics.off()

```

```{r, results='asis'}
plot(coinfxnplotObj)
```


#### Cluster Level Prevalences-Interactions
```{r}
mp <- readRDS(file = "data/derived_data/basic_cluster_mapping_data.rds")
ge <- readRDS("data/raw_data/dhsdata/VivIDge.RDS")

pfpvclst <- mp %>% 
  dplyr::filter(plsmdmspec %in% c("pfldh", "pv18s") & maplvl == "hv001") %>% 
  dplyr::ungroup() %>% 
  dplyr::select(c("plsmdmspec", "data")) 

# issue with casting from sf
pf <- pfpvclst$data[[1]]
pfclust <- cbind.data.frame(species = "pf", pf) %>% 
  dplyr::select(c("species", "hv001", "plsmdprev", "n"))
pv <- pfpvclst$data[[2]]
pvclust <- cbind.data.frame(species = "pv", pv) %>% 
  dplyr::select(c("species", "hv001", "plsmdprev", "n"))

pfpvclst <- left_join(pfclust, pvclust, by = c("hv001", "n")) %>% 
  dplyr::left_join(., y = ge, by = "hv001")


```

```{r, results='asis'}

pfpvclst %>% 
  ggplot() + 
  geom_point(aes(x=plsmdprev.x, y = plsmdprev.y, size = n)) +
  geom_smooth(aes(x=plsmdprev.x, y = plsmdprev.y, weight = n), method=loess) +
  facet_wrap(~ urban_rura) +
  xlab("Pfalciparum") + ylab("Pvivax") + 
  labs(title ="Cluster Level Prevalences Seperated \n by Urbanicity",
       caption = "Loess line and point sizes are weighted by cluster size") +
  theme_bw() +
  theme(legend.position = "none",
        plot.title = element_text(vjust = 0.5, hjust = 0.5))



```



## Ape Distribution  vs. _P. vivax_  


```{r, results='asis'}
#......................
# vivid pieces 
#......................
dt <- readRDS("data/derived_data/vividepi_recode_completecases.rds")
dtsrvy <- makecd2013survey(survey = dt)
# DRC
DRCprov <- readRDS("data/map_bases/vivid_DRCprov.rds")

# pv prev
clstprev <- dtsrvy %>% 
  dplyr::mutate(count = 1) %>% 
  dplyr::group_by(hv001) %>% 
  dplyr::summarise(n = srvyr::survey_total(count, vartype = c("se", "ci")),
                   pv18sn = srvyr::survey_total(pv18s, vartype = c("se", "ci")),
                   pfldhn = srvyr::survey_total(pfldh, vartype = c("se", "ci"))) %>% 
  dplyr::mutate(
    pv18sbinomtest = purrr::map2(pv18sn, n, function(x,y)
    {binom.test(x = round(x), n = round(y))}),
    pv18sprev = pv18sn/n,
    pvconfint = purrr::map(pv18sbinomtest, "conf.int"),
    pv18sL95 = purrr::map_dbl(pvconfint, 1),
    pv18sU95 =purrr::map_dbl(pvconfint, 2))

# add in longnum
genosf <- ge %>% 
  dplyr::mutate(longnum = sf::st_coordinates(geometry)[,1],
                latnum = sf::st_coordinates(geometry)[,2])
sf::st_geometry(genosf) <- NULL
# bring together
pvpos_cases <- dplyr::left_join(clstprev, genosf, by = "hv001") %>% 
  dplyr::filter(pv18sprev != 0)
#......................
# bring in apes
#......................
ape <- readRDS("data/derived_data/drc_ape.rds")
ape <- sf::st_intersection(ape, DRCprov)

apeMainFig <- ggplot() +
  geom_sf(data = DRCprov, color = "#737373", fill = "#525252") +
  geom_sf(data = ape, aes(fill = species), color = NA, alpha = 0.6) +
  scale_fill_manual("Non-Human \n Ape Habitat", 
                    values = c("#316F65", "#4D8A5F", "#71A473", "#76BC43")) + 
  geom_point(data = pvpos_cases,
             aes(x = longnum, y = latnum, 
                 color = pv18sprev), alpha = 0.9) +
  scale_color_distiller("Vivax \n Prevalence", type = "div", palette = "RdYlBu",
                       na.value = NA) +
  theme_void() + 
  theme(legend.title = element_text(size = 10, face = "bold", hjust = 0.5),
        legend.text = element_text(size = 8),
        legend.position = "right")


```

### Permutation Test for _P. vivax_ vs. Ape Distribution 

Data will be simulated by randomly assigning clusters as ape or not territories and then calculating the prevalence of Pv within ape and non-ape regions. 

```{r}
# how many clusters do apes overlap?
ape.range <- sf::st_union(ape$geometry)
ape.clusters <- sf::st_intersection(ge, ape.range)

# how many clusters do chimp and gorillas overlap?
chimpgor.range <- ape %>% 
  dplyr::filter(species != "Pan paniscus") %>% 
  dplyr::select(geometry) %>% 
  sf::st_union(.)
chimpgor.clusters <- sf::st_intersection(ge, chimpgor.range)

```

There are `r length(ape.clusters)` clusters that overlap with apes and `r length(chimpgor.clusters)` clusters that overlap with chimpanzee and gorillas.

#### All Apes 

```{r, results='asis'}

#......................
# read in 
#......................
ape.range.iters <- readRDS("analyses/08-nonparam_riskfacts/perm_rets/all_ape_range_iters.RDS")

# observed
real.ape.clstrprev <- dt %>% 
  dplyr::filter(hv001 %in% ape.clusters$hv001)

real.ape.clstrprev <- mean(real.ape.clstrprev$pv18s)

# plot out
hist(ape.range.iters$ape_overlap_prev, breaks = 50, 
     main = "Simulated Pvivax Prevelance \n within Ape Clusters")
abline(v = real.ape.clstrprev, col = "red")

```

Assuming a one-sided test that ape clusters should have more _P. vivax_, we can get a monte-carlo P-value of approximately `r round(mean(ape.range.iters$ape_overlap_prev > real.ape.clstrprev), 2)`. Obviously not significant from plot and maps.


#### Chimpanzee & Gorillas
Note, Bonobos have recently been shown to also harbor _P. vivax-like_ strains but mostly at a concentrated field site, Tshuapa–Lomami–Lualaba (TL2), near the Lomami River [Liu et al. 2018](https://www.nature.com/articles/s41467-017-01798-5)

```{r, results='asis'}

#......................
# read in 
#......................
chimpgor.range.iters <- readRDS("analyses/08-nonparam_riskfacts/perm_rets/chimp_gor_range_iters.RDS")

# observed
real.chimpgor.clstrprev <- dt %>% 
  dplyr::filter(hv001 %in% chimpgor.clusters$hv001)
real.chimpgor.clstrprev <- mean(real.chimpgor.clstrprev$pv18s)

# plot out
hist(chimpgor.range.iters$chimpgor_overlap_prev, breaks = 50, 
     main = "Simulated Pvivax Prevelance \n within Chimp & Gor Clusters")
abline(v = real.chimpgor.clstrprev, col = "red")

```

As above, assuming a one-sided test that chimpanzee and gorilla clusters should have more _P. vivax_, we can get a monte-carlo P-value of approximately `r round(mean(chimpgor.range.iters$chimpgor_overlap_prev > real.chimpgor.clstrprev), 2)`. Obviously not significant from plot and maps.


```{r}
##############################
# Ape Overlap
##############################
jpeg("results/figures/pv-ape-overlap-crude_maps1x1.jpg", width = 11, height = 8, units = "in", res = 500)
apeMainFig
graphics.off()


```

```{r, results = 'asis', fig.width= 12, fig.height=12}
apeMainFig
```

## Airplane - Importation Corr
```{r}
#......................
# import data
#......................
airports <- readr::read_csv("data/raw_data/hotosm_data/hotosm_airports/hotosm_cd-airports.csv") %>%
  dplyr::filter(type %in% c("large_airport", "medium_airport"))  
airports <- sf::st_as_sf(airports, coords = c("longitude_deg", "latitude_deg"),
                         crs = "+init=epsg:4326")
# drc prov
DRCprov <- sf::st_as_sf(readRDS("data/map_bases/gadm/gadm36_COD_1_sp.rds"))

# cities
drccities <- readr::read_csv("data/map_bases/DRC_city_coordinates.csv") %>% 
  dplyr::filter(population > 1e5)

#......................
# vivid items
#......................
dt <- readRDS("data/derived_data/vividepi_recode_completecases.rds")
dtsrvy <- makecd2013survey(survey = dt)
ge <- readRDS(file = "data/raw_data/dhsdata/VivIDge.RDS")

#......................
# get prev 
#......................
clstprev <- dtsrvy %>% 
  dplyr::mutate(count = 1) %>% 
  dplyr::group_by(hv001) %>% 
  dplyr::summarise(n = srvyr::survey_total(count, vartype = c("se", "ci")),
                   pv18sn = srvyr::survey_total(pv18s, vartype = c("se", "ci")),
                   pfldhn = srvyr::survey_total(pfldh, vartype = c("se", "ci"))) %>% 
  dplyr::mutate(
    pv18sbinomtest = purrr::map2(pv18sn, n, function(x,y)
    {binom.test(x = round(x), n = round(y))}),
    pv18sprev = pv18sn/n,
    pvconfint = purrr::map(pv18sbinomtest, "conf.int"),
    pv18sL95 = purrr::map_dbl(pvconfint, 1),
    pv18sU95 =purrr::map_dbl(pvconfint, 2)
  )

#......................
# get cluster and airport distances
#......................
clst_air_dist <- sf::st_distance(ge, airports)
clst_air_dist <- tibble::tibble(
  hv001 = ge$hv001,
  mindist = apply(clst_air_dist, 1, min))

# bring together
prev_air <- dplyr::left_join(clstprev, clst_air_dist, by = "hv001") %>% 
  dplyr::mutate(mindist = mindist/1e3)


```

#### DRC Airports
```{r, results='asis'}
inset <- airports %>% 
  dplyr::mutate(longnum = sf::st_coordinates(geometry)[,1],
                latnum = sf::st_coordinates(geometry)[,2]) %>% 
  ggplot() +
  geom_sf(data = DRCprov, color = "#737373", fill = "#525252") +
  geom_point(aes(x = longnum, y = latnum), color = "#ED2C31", 
             size = 2, alpha = 0.8, shape = 17) +
  theme_void()

```


#### Correlation of Prev and Airports
```{r, results='asis'}
pmain <- prev_air %>% 
  dplyr::filter(pv18sprev != 0) %>% 
  ggplot() + 
  geom_pointrange(aes(x = mindist, y = pv18sprev,
                      ymin = pv18sL95, ymax = pv18sU95),
                  alpha = 0.5) + 
  ylab("Vivax Prevalence") +
  xlab("Min. Airport Dist. (km)") +
  vivid_theme + 
  theme(axis.line = element_line(size = 1))

# bring together
AirportMainFig <- cowplot::ggdraw() +
  cowplot::draw_plot(pmain,
                     x = 0, y = 0, width = 1, height = 0.95, scale = 1) +
  cowplot::draw_plot(inset, x = 0.7, y = 0.55,
                     width = 0.3, height = 0.3)



```


## SatScan
Cedar doing this locally. 
```{r}
satscanspace <- ggplot() + theme_void()
```

## Bring Together
```{r}

apeMainFig <- apeMainFig +
  theme(plot.margin = margin(0, 0, 0, 0.9, "cm"))

toprow <- coinfxnplotObj
bottomrow <- cowplot::plot_grid(apeMainFig, AirportMainFig, satscanspace,
                                ncol = 3, labels = c("(B)", "(C)", "(D)"))
mainfig <- cowplot::plot_grid(toprow, bottomrow, 
                   nrow = 2, rel_heights = c(0.8, 1), 
                   labels = c("(A)", ""))

jpeg("results/figures/non_param_riskfactors.jpg", width = 11, height = 8, units = "in", res = 800)
mainfig
graphics.off()

svglite::svglite("results/figures/non_param_riskfactors.svg", width = 11, height = 8)
mainfig
graphics.off()

```
```{r, results='asis'}
plot(mainfig)
```