---
output: html_document
editor_options: 
  chunk_output_type: console
---

# Univariate and Bivariate Summary Statistics

```{r}
#------------------------------------------------------------------ 
# Purpose of this script is to do basic bivariate analyses
#------------------------------------------------------------------ 
source("~/Documents/GitHub/VivID_Epi/R/00-functions_basic.R") 
source("~/Documents/GitHub/VivID_Epi/R/00-functions_epi.R") 
library(tidyverse)
library(survey)
library(srvyr) #wrap the survey package in dplyr syntax
devtools::install_github("kaz-yos/tableone")
library(tableone)
options(scipen=999)


#......................
# Import Data
#......................
dt <- readRDS("~/Documents/GitHub/VivID_Epi/data/derived_data/vividepi_recode_completecases.rds")
dcdr <- readxl::read_excel(path = "~/Documents/GitHub/VivID_Epi/model_datamaps/sub_DECODER_covariate_map_v3.xlsx", sheet = 1) %>% 
  dplyr::mutate(risk_factor_raw = ifelse(is.na(risk_factor_raw), "n", risk_factor_raw),
                risk_factor_model = ifelse(is.na(risk_factor_model), "n", risk_factor_model))

dtsrvy <- makecd2013survey(survey = dt)

ge <- readRDS(file = "~/Documents/GitHub/VivID_Epi/data/raw_data/dhsdata/VivIDge.RDS")

```


## Prevalence

### National Prevalence
Fit basic intercept weighted-glm to derive weighted national prevalence. 

```{r, results='asis'}

#-------------------------------------------------------- 
# Basic Descriptive Statistics
#-------------------------------------------------------- 
# national prevalence
sumnums <- dtsrvy %>% 
  dplyr::mutate(count = 1) %>% 
  dplyr::summarise(n = srvyr::survey_total(count, vartype = c("se", "ci")),
                   pvn = srvyr::survey_total(pv18s, vartype = c("se", "ci")),
                   pfn = srvyr::survey_total(pfldh, vartype = c("se", "ci")))


drcpv <- survey::svyglm(pv18s ~ 1, design = dtsrvy)
drcpv <- broom::tidy(drcpv, conf.int = T)

# national prevalence
drcpf <- survey::svyglm(pfldh ~ 1, design = dtsrvy)
drcpf <- broom::tidy(drcpf, conf.int = T)

rbind.data.frame( cbind.data.frame(species = "Pv", drcpv),
                  cbind.data.frame(species = "Pf", drcpf)
                  ) %>% 
  dplyr::select(-c("term")) %>% 
  dplyr::rename(Prevalence = estimate) %>% 
  knitr::kable()
  

```

### Cluster Level Prevalence 
**N.B. Everyone is weighted the same in the cluster, which results in the same cluster level prevalences whether you consider weights or not**. However, this will results in  slightly different numerator (e.g. $n_numerator$) and denominators between the weighted and unweighted approach. Caution is warranted when reporting weighted versus unweighted Ns and Standard Errors at the cluster-level for this reason. 
  
NB Given the small Ns (<30) in many of the clusters, we cannot approximate the binomial distribution as a normal distribution, and thus our confidence interval calculations need to be performed with exact methods to avoid boundary issues (e.g. prevalences < 0 or > 100%). I used a logit transformation and the t-distribution to estimate these CIs.    
    
See the _Appendix_ for individual cluster counts.

```{r, results='asis', fig.align='center', fig.width=11, fig.height=8}

# cluster-level prevalence, because everyone is weighted the same in the cluster, don't use weights here
# note, the numerators will be slightly different (e.g. N) but the denomminators adjust for this
# Going to report whole numbers/unadjusted for clusters
clst <- dt %>%
  dplyr::mutate(count = 1) %>%
  dplyr::group_by(hv001) %>%
  dplyr::summarise(n = n(),
                   pv18sn = sum(pv18s),
                   pv18sprev = mean(pv18s),
                   pv18sse = sqrt(pv18sn * pv18sprev * (1 - pv18sprev)) / sqrt(pv18sn),
                   pv18sL95 = getCI_from_logit_transfrom(succeses = pv18sn, n = n, tol = 0, alpha = 0.05)[1],
                   pv18sU95 = getCI_from_logit_transfrom(succeses = pv18sn, n = n, tol = 0, alpha = 0.05)[2],

                   pfldhn = sum(pfldh),
                   pfldhprev = mean(pfldh),
                   pfldhse = sqrt(pfldhn * pfldhprev * (1 - pfldhprev)) / sqrt(pfldhn),
                   pfldhL95 = getCI_from_logit_transfrom(succeses = pfldhn, n = n, tol = 0, alpha = 0.05)[1],
                   pfldhU95 = getCI_from_logit_transfrom(succeses = pfldhn, n = n, tol = 0, alpha = 0.05)[2],

                   )




# ignore 95% CI but want the weighted numerator and denominator for the paper 
clstprev <- dtsrvy %>% 
  dplyr::mutate(count = 1) %>% 
  dplyr::group_by(hv001) %>% 
  dplyr::summarise(n = srvyr::survey_total(count, vartype = c("se", "ci")),
                   pvn = srvyr::survey_total(pv18s, vartype = c("se", "ci")),
                   pfn = srvyr::survey_total(pfldh, vartype = c("se", "ci")),
                   
                   pvprev = srvyr::survey_mean(pv18s, vartype = c("se", "ci")),
                   pfprev = srvyr::survey_mean(pfldh, vartype = c("se", "ci"))
                   ) %>% 
  dplyr::select(c("n", "pvn", "pfn", "pvprev", "pfprev"))



# extra items for making a pretty plot
dhsreg <- dt %>% 
  dplyr::left_join(., ge, by = "hv001") %>% 
  dplyr::select(c("hv001", "adm1fipsna")) %>% 
  dplyr::mutate(prov = as.character( haven::as_factor(adm1fipsna) ),
                prov = tools::toTitleCase(prov)) %>% 
  dplyr::filter(!duplicated(.)) %>% 
  dplyr::select(-c("adm1fipsna"))


clst.prev.plotObj <- clst %>% 
  dplyr::left_join(., y = dhsreg, by = "hv001") %>% 
  dplyr::select(c("prov", "hv001", "pv18sprev", "pv18sL95", "pv18sU95",
                  "pfldhprev", "pfldhL95", "pfldhU95")) %>% 
  tidyr::gather(., key = "estlevel", value = "est", 3:ncol(.)) %>% 
  dplyr::mutate(species = ifelse(grepl("pv", estlevel), "Pv", "Pf")) %>% 
  dplyr::select(c("prov", "hv001", "species", dplyr::everything())) %>% 
  dplyr::mutate(estlevel = gsub("pv18s", "", estlevel),
                estlevel= gsub("pfldh", "", estlevel)) %>% 
  tidyr::spread(., key = "estlevel", value = "est", 4:5) %>% 
  ggplot() + 
  geom_pointrange(aes(x = factor(hv001), y=prev, ymin=L95, ymax=U95, color = factor(species)), size =0.5, alpha = 0.5) +
  coord_flip() + 
  facet_wrap(~prov, scales = "free", ncol = 4) +
  scale_color_viridis_d("Species") + 
  ggtitle("Cluster-Level Prevelance of Pv and Pf Malaria") +
  vivid_theme + 
  theme(plot.title = element_text(family = "Helvetica", face = "bold", hjust = 0.5, size = 12),
        legend.position = "bottom",
        legend.title = element_text(family = "Helvetica", face = "bold", vjust = 0.5, size = 8),
        legend.text = element_text(family = "Helvetica", hjust = 0.5, vjust = 0.5, size = 7, angle = 0),
        strip.text = element_text(family = "Helvetica", hjust = 0.5, size = 6, face = "bold"),
        axis.title = element_blank(),
        axis.text.y = element_blank(),
        axis.text.x = element_text(family = "Helvetica", hjust = 0.5, size = 6, angle = 90),
        axis.ticks.y = element_blank()
  )


plot(clst.prev.plotObj)

dir.create(path = "~/Documents/GitHub/VivID_Epi/results/figures/", recursive = T)
jpeg(filename = "~/Documents/GitHub/VivID_Epi/results/figures/cluster_prevalence_pointranges.jpg",
     width = 11, height = 8, units = "in", res=500)
plot(clst.prev.plotObj)
graphics.off()


```

## Duffy Negativity
### Counts and Prevalences
```{r}
# three samples with duffy negativity
duffypos <- tolower(c("C1T5C", "G9M2E", "J3Q9M"))

duff <- dt %>% 
  dplyr::mutate(duffy = ifelse(hivrecode_barcode%in% duffypos, 1, 0)) %>% 
  dplyr::summarise(
    duff_total = sum(duffy)
  ) 

duffn <- sum(dt$pv18s)
duff <- duff %>% 
  dplyr::mutate(duff_total = mean(duff_total),
                duff_prev = duff_total/duffn * 100,
                duffse = sqrt( duff_total * (duff_total/duffn) * (1-(duff_total/duffn)) ),
                duffL95 = getCI_from_logit_transfrom(succeses = duff_total, n = duffn, tol = 0, alpha = 0.05)[1] * 100,
                duffU95 = getCI_from_logit_transfrom(succeses = duff_total, n = duffn, tol = 0, alpha = 0.05)[2] * 100
  )


# weighted
duffn <- sum( dt$hiv05_wi[dt$pv18s == 1] )
duff_wi <- dtsrvy %>% 
  dplyr::mutate(duffy = ifelse(hivrecode_barcode%in% duffypos, 1, 0)) %>% 
  dplyr::summarise(
    duff_wi_total = srvyr::survey_total(duffy, vartype = "ci")
  ) 

duff_wi <- duff_wi %>% 
  dplyr::mutate(duff_wi_total = mean(duff_wi_total),
                duff_wi_prev = duff_wi_total/duffn * 100,
                duffse = sqrt( duff_wi_total * (duff_wi_total/duffn) * (1-(duff_wi_total/duffn)) ),
                duffL95 = getCI_from_logit_transfrom(succeses = duff_wi_total, n = duffn, tol = 0, alpha = 0.05)[1] * 100,
                duffU95 = getCI_from_logit_transfrom(succeses = duff_wi_total, n = duffn, tol = 0, alpha = 0.05)[2] * 100
  )



```

Note, prevalences below are in percentages.
```{r, results='asis'}

duff %>% 
  dplyr::mutate_if(is.numeric, round, 2) %>% 
knitr::kable(.)

duff_wi %>% 
  dplyr::mutate_if(is.numeric, round, 2) %>% 
knitr::kable(.)

```


## Coinfections
### Unweighted Counts
```{r, results='asis'}

# coinfections unweighted
coinfxn <- dt %>% 
  dplyr::mutate(pfmono =  ifelse(pfldh == 1 & pv18s == 0 & po18s == 0, 1, 0),
                pvmono =  ifelse(pfldh == 0 & pv18s == 1 & po18s == 0, 1, 0),
                pomono =  ifelse(pfldh == 0 & pv18s == 0 & po18s == 1, 1, 0),
                pfpv =  ifelse(pfldh == 1 & pv18s == 1 & po18s == 0, 1, 0),
                pfpo =  ifelse(pfldh == 1 & pv18s == 0 & po18s == 1, 1, 0),
                pvpo =  ifelse(pfldh == 0 & pv18s == 1 & po18s == 1, 1, 0),
                pfpvpo =  ifelse(pfldh == 1 & pv18s == 1 & po18s == 1, 1, 0)
  ) %>% 
  dplyr::summarise(
    "pf" = sum(pfmono),
    "pv" = sum(pvmono),
    "po" = sum(pomono),
    "pf/pv" = sum(pfpv),
    "pf/po" = sum(pfpo),
    "pv/po" = sum(pvpo),
    "pf/pv/po" = sum(pfpvpo)
  )

knitr::kable(coinfxn)



```

### Weighted Counts
```{r, results='asis'}
# need weighed counts
coinfxn.wi <- dtsrvy %>% 
  dplyr::mutate(pfmono =  ifelse(pfldh == 1 & pv18s == 0 & po18s == 0, 1, 0),
                pvmono =  ifelse(pfldh == 0 & pv18s == 1 & po18s == 0, 1, 0),
                pomono =  ifelse(pfldh == 0 & pv18s == 0 & po18s == 1, 1, 0),
                pfpv =  ifelse(pfldh == 1 & pv18s == 1 & po18s == 0, 1, 0),
                pfpo =  ifelse(pfldh == 1 & pv18s == 0 & po18s == 1, 1, 0),
                pvpo =  ifelse(pfldh == 0 & pv18s == 1 & po18s == 1, 1, 0),
                pfpvpo =  ifelse(pfldh == 1 & pv18s == 1 & po18s == 1, 1, 0)
  ) %>% 
  dplyr::summarise(
    "pf" = srvyr::survey_total(x=pfmono),
    "pv" = srvyr::survey_total(x=pvmono),
    "po" = srvyr::survey_total(x=pomono),
    "pf/pv" = srvyr::survey_total(x=pfpv),
    "pf/po" = srvyr::survey_total(x=pfpo),
    "pv/po" = srvyr::survey_total(x=pvpo),
    "pf/pv/po" = srvyr::survey_total(x=pfpvpo)
  ) %>% 
  dplyr::select(-c(dplyr::ends_with("_se")))

knitr::kable(coinfxn.wi)

```

# Table One(s)
## _P. vivax_ Infected vs. Uninfected
```{r, results='asis'}
#------------------------------------------------------------------------------------- 
# TABLE ONE -- bivariate analyses, descriptive
#------------------------------------------------------------------------------------- 

#.......................
# Pvivax 
#.......................
pvivrskfctr <- dcdr$column_name[dcdr$risk_factor_raw == "y"]

pvivtbl1 <- tableone::svyCreateTableOne(data = dtsrvy,
                                        strata = "pv18s_fctb",
                                        vars = pvivrskfctr,
                                        includeNA = T,
                                        test = F)

tableone::kableone(pvivtbl1)

```

## _P. falciparum_ Infected vs. Uninfected
```{r, results='asis'}

#.......................
# Pfalciparum 
#.......................
pfalrskfctr <- dcdr$column_name[dcdr$risk_factor_raw == "y" & dcdr$column_name != "pfldh_fctb" ]
pfalrskfctr <- c("pv18s_fctb", pfalrskfctr)

pfaltbl1 <- tableone::svyCreateTableOne(
  data = dtsrvy,
  strata = "pfldh_fctb",
  vars = pfalrskfctr,
  includeNA = T,
  test = F)

tableone::kableone(pfaltbl1)

```

## Infected with Malaria vs. Not-Infected
```{r, results='asis'}
#------------------------------------------------------------------------------------
# Make Pv Cases, Pf Cases, and Non-Cases Table
#------------------------------------------------------------------------------------
dt.cases <- dt %>% 
  dplyr::mutate(
    case = ifelse(( pv18s == 1 | pfldh ==1 ), 1, 0),
    case_fctb = factor(case, levels = c(0,1), labels = c("noncase", "case"))
  )

dt.cases.srvy <- makecd2013survey(dt.cases)
casesrskfctr <- dcdr$column_name[dcdr$risk_factor_raw == "y"]
casestbl1 <- tableone::svyCreateTableOne(
  data = dt.cases.srvy,
  strata = "case_fctb",
  vars = casesrskfctr,
  includeNA = T,
  test = F)

tableone::kableone(casestbl1)

```

# Table Two(s)
N.B. We have no scaled (i.e. mean-centered and standardized) all continous variables with the exception of the wlth variable, as it was already a factor score. Dichotomized variables have the presumed protective level as the reference level.   
  
N.B. Parametric association test using GEE (`svyglm` is performing GEE with the sampling weights considered "repeat" observations). Given that we are not considering confounding in these estimates, they are purely assocations and should not be overly interpreted. 

## _P. vivax_ Risk Bivariate **Associations**
```{r, results='asis'}

#-----------------------------------------------------------------------------------------
# TABLE 2
# Parametric, Bivariate Analysis
# note, that svyglm is really doing GEE
#----------------------------------------------------------------------------------------

# note overwriting risk factors to have scaled models now
#.......................
# Pvivax 
#.......................
pvivrskfctr <- dcdr$column_name[dcdr$risk_factor_model == "y"]
pvivrskfctr_models <- data.frame(outcome = rep("pv18s", length(pvivrskfctr)), 
                               covar = pvivrskfctr, stringsAsFactors=FALSE)

pvivrskfctr_models$glmlogit <- purrr::pmap(pvivrskfctr_models, .f=fitsvyglmlogit)
pvivrskfctr_models$glmlogit_tidy <- purrr::map(pvivrskfctr_models$glmlogit,
                                             .f=function(x){
                                             broom::tidy(x, exponentiate=TRUE, conf.int=TRUE)}
                                             )
pvivrskfctr_est <- pvivrskfctr_models$glmlogit_tidy %>% 
  bind_rows() %>% filter(term != "(Intercept)") %>% 
  mutate_if(is.numeric, round, 2)

knitr::kable(pvivrskfctr_est)

```

## _P. falciparum_ Risk Bivariate **Associations**
```{r, results='asis'}
#.......................
# Pfalciparum 
#.......................
pfalrskfctr <- dcdr$column_name[dcdr$risk_factor_model == "y" & dcdr$column_name != "pfldh_fctb"]
pfalrskfctr <- c("pv18s_fctb", pfalrskfctr)

pfalrskfctr_models <- data.frame(outcome = rep("pfldh", length(pfalrskfctr)), 
                               covar = pfalrskfctr, stringsAsFactors=FALSE)

pfalrskfctr_models$glmlogit <- purrr::pmap(pfalrskfctr_models, .f=fitsvyglmlogit)


pfalrskfctr_models$glmlogit_tidy <- purrr::map(pfalrskfctr_models$glmlogit,
                                             .f=function(x){
                                             broom::tidy(x, exponentiate=TRUE, conf.int=TRUE)})


pfalrskfctr_est <- pfalrskfctr_models$glmlogit_tidy %>% 
  bind_rows() %>% filter(term != "(Intercept)") %>% 
  mutate_if(is.numeric, round, 2)

knitr::kable(pfalrskfctr_est)


```

### Pretty Table
Combine tables 1s and 2s to make a prettier output. 
```{r}
#------------------------------------------------------------------
# Combine Table 1 and 2
#------------------------------------------------------------------ 

#.......................
# Pvivax
#.......................
pvivtbl1df <- tableone2dataframe(pvivtbl1, columnnames = c("Covariates",
                                                           "Pvivax-Negative",
                                                           "Pvivax-Positive",
                                                           "matchcol"))
pvivtbl1df <- dcdr %>% 
  dplyr::select(c("column_name", "var_label")) %>% 
  dplyr::rename(matchcol = column_name) %>% 
  dplyr::left_join(pvivtbl1df, ., by = "matchcol") %>% 
  dplyr::select(c("var_label", dplyr::everything()))
 


pvivriskfactortable <- mergetableone2table(tableonedf = pvivtbl1df,
                                           tabletwoestdf = pvivrskfctr_est)

pvivriskfactortable <- pvivriskfactortable %>% 
  dplyr::select(-c("matchcol"))

#.......................
# Pfalciparum 
#.......................
pfaltbl1df <- tableone2dataframe(pfaltbl1, columnnames = c("Covariates",
                                                           "Pfalciparum-Negative",
                                                           "Pfalciparum-Positive",
                                                           "matchcol"))

pfaltbl1df <- dcdr %>% 
  dplyr::select(c("column_name", "var_label")) %>% 
  dplyr::rename(matchcol = column_name) %>% 
  dplyr::left_join(pfaltbl1df, ., by = "matchcol") %>% 
  dplyr::select(c("var_label", dplyr::everything()))


pfalriskfactortable <- mergetableone2table(tableonedf = pfaltbl1df,
                                           tabletwoestdf = pfalrskfctr_est)


pfalriskfactortable <- pfalriskfactortable %>% 
  dplyr::select(-c("matchcol"))



#.......................
# Cases to DF 
#.......................
casestbl1df <- tableone2dataframe(casestbl1, columnnames = c("Covariates",
                                                           "Case-Negative",
                                                           "Case-Positive",
                                                           "matchcol"))

casestbl1df <- dcdr %>% 
  dplyr::select(c("column_name", "var_label")) %>% 
  dplyr::rename(matchcol = column_name) %>% 
  dplyr::left_join(casestbl1df, ., by = "matchcol") %>% 
  dplyr::select(c("var_label", dplyr::everything()))




```

## _P. vivax_ Risk Association Table 
```{r, results='asis'}
DT::datatable(pvivriskfactortable, 
              rownames = F,
              options = list(
                searching = F,
                pageLength = 30,
                dom = 'Bfrtip', 
                buttons = c('csv')),
              caption = htmltools::tags$caption(
                style = 'caption-side: bottom; text-align: center;',
                "P vivax Risk Factor Table with Counts and Prevalence Odds Ratio Bivariate Associations"))

```


## _P. falciparum_ Risk Association Table 
```{r, results='asis'}
DT::datatable(pfalriskfactortable, 
              rownames = F,
              options = list(
                searching = F,
                pageLength = 30,
                dom = 'Bfrtip', 
                buttons = c('csv')),
              caption = htmltools::tags$caption(
                style = 'caption-side: bottom; text-align: center;',
                "P falciparum Risk Factor Table with Counts and Prevalence Odds Ratio Bivariate Associations"))

```


## Malaria Risk Association Figure

```{r, results='asis', fig.align='center', fig.width=8, fig.height=8}
#...................................................
# Tidy
#...................................................
pvriskest <- pvivrskfctr_models$glmlogit_tidy %>% 
  bind_rows() %>% filter(term != "(Intercept)") %>% 
  mutate_if(is.numeric, round, 2) %>% 
  dplyr::rename(column_name = term) %>% 
  dplyr::mutate(
     column_name = ifelse(grepl("_fctb_clst", column_name),
                         stringr::str_extract(column_name, "[ -~]+_fctb_clst"),
                         column_name),
    column_name = ifelse(!grepl("_fctb_clst", column_name) & grepl("_fctb", column_name),
                         stringr::str_extract(column_name, "[ -~]+_fctb"),
                         column_name)
  )

pvriskest <- dplyr::left_join(pvriskest, dcdr, by = "column_name")
orderrf <- pvriskest %>% 
  dplyr::arrange(level) %>% 
  dplyr::select(abridged_var_label) %>% 
  unlist(.)

# PF
pfriskest <- pfalrskfctr_models$glmlogit_tidy %>% 
  bind_rows() %>% filter(term != "(Intercept)") %>% 
  mutate_if(is.numeric, round, 2) %>% 
  dplyr::rename(column_name = term)  %>% 
  dplyr::mutate(
     column_name = ifelse(grepl("_fctb_clst", column_name),
                         stringr::str_extract(column_name, "[ -~]+_fctb_clst"),
                         column_name),
    column_name = ifelse(!grepl("_fctb_clst", column_name) & grepl("_fctb", column_name),
                         stringr::str_extract(column_name, "[ -~]+_fctb"),
                         column_name)
  )

pfriskest <- dplyr::left_join(pfriskest, dcdr, by = "column_name")
orderrf <- pfriskest %>% 
  dplyr::arrange(level) %>% 
  dplyr::select(abridged_var_label) %>% 
  unlist(.)

#...................................................
# Make Plots
#...................................................

pv_bivar_rf_plot <- pvriskest %>% 
  dplyr::mutate(abridged_var_label = factor(abridged_var_label, levels = orderrf, ordered = T)) %>% 
  ggplot() +
  geom_hline(yintercept = 1, color = "#cb181d", linetype = "dashed") +
  geom_pointrange(aes(x = abridged_var_label, y = estimate, 
                      ymin = conf.low, ymax = conf.high,
                      color = factor(level))) +
  scale_color_manual("Level", values = c("#0868ac", "#4eb3d3")) +
  coord_flip() + 
  ggtitle(expression(bolditalic("P. vivax"))) +
  ylab("Prevalence Odds Ratio") + 
  theme(
    plot.title =  element_text(family = "Helvetica", face = "bold", vjust = 0.5, hjust = 0.5, size = 14),
    axis.title.x = element_text(family = "Helvetica", face = "bold", vjust = 0.5, hjust = 0.5, size = 12, angle = 45),
    axis.text = element_text(family = "Helvetica", vjust = 0.5, hjust = 0.5, size = 11),
    axis.title.y = element_blank(),
    legend.title = element_text(family = "Helvetica", face = "bold", vjust = 0.5, hjust = 0.5, size = 12),
    legend.text = element_text(family = "Helvetica", vjust = 0.5, hjust = 0.5, size = 10, angle = 0),
    legend.position = "right",
    axis.line.x = element_line(color = "black", size = 1.5),
    axis.line.y = element_blank(),
    axis.ticks.y = element_blank(),
    panel.background = element_rect(fill = "transparent"),
    plot.background = element_rect(fill = "transparent"),
    panel.grid = element_blank(),
    panel.border = element_blank())
    

pf_bivar_rf_plot <- pfriskest %>% 
  dplyr::mutate(abridged_var_label = factor(abridged_var_label, levels = orderrf, ordered = T)) %>%
  ggplot() +
  geom_hline(yintercept = 1, color = "#cb181d", linetype = "dashed") +
  geom_pointrange(aes(x = abridged_var_label, y = estimate, 
                      ymin = conf.low, ymax = conf.high,
                      color = factor(level))) +
  scale_color_manual("Level", values = c("#006d2c", "#41ae76")) +
  ylim(c(0,2)) + 
  coord_flip() + 
  ggtitle(expression(bolditalic("P. falciparum"))) +
  ylab("Prevalence Odds Ratio") + 
  theme(
    plot.title =  element_text(family = "Helvetica", face = "bold", vjust = 0.5, hjust = 0.5, size = 14),
    axis.title.x = element_text(family = "Helvetica", face = "bold", vjust = 0.5, hjust = 0.5, size = 12, angle = 45),
    axis.text = element_text(family = "Helvetica", vjust = 0.5, hjust = 0.5, size = 11),
    axis.title.y = element_blank(),
    legend.title = element_text(family = "Helvetica", face = "bold", vjust = 0.5, hjust = 0.5, size = 12),
    legend.text = element_text(family = "Helvetica", vjust = 0.5, hjust = 0.5, size = 10, angle = 0),
    legend.position = "right",
    axis.line.x = element_line(color = "black", size = 1.5),
    axis.line.y = element_blank(),
    axis.ticks.y = element_blank(),
    panel.background = element_rect(fill = "transparent"),
    plot.background = element_rect(fill = "transparent"),
    panel.grid = element_blank(),
    panel.border = element_blank())

cowplot::plot_grid(pv_bivar_rf_plot, 
                   pf_bivar_rf_plot, 
                   nrow = 1, 
                   align = "h",
                   labels = c("A", "B"))


# svglite::svglite(file = "results/figures/Figure1B.svg")
jpeg("~/Documents/GitHub/VivID_Epi/results/figures/PfPv_Bivariate_dotplotRR.jpg", 
     width = 11, height = 8, units = "in", res = 500)
cowplot::plot_grid(pv_bivar_rf_plot, 
                   pf_bivar_rf_plot, 
                   nrow = 1, 
                   align = "h",
                   labels = c("A", "B"))
graphics.off()


```

```{r}

#-----------------------------------------------------------------------------
# housekeeping -- Save out
#-----------------------------------------------------------------------------
save(pvivtbl1df, pfaltbl1df, # table one output 
     pvivrskfctr_models, pfalrskfctr_models, # model datatframes
     pvivriskfactortable, pfalriskfactortable, # final out table for report
     casestbl1df, # for prettier table 1
     file = "~/Documents/GitHub/VivID_Epi/results/bivariate_model_results.rda")


#-----------------------------------------------------------------------------
# housekeeping -- write out
#-----------------------------------------------------------------------------
# Case/NonCase Dist Tables
dir.create(path = "~/Documents/GitHub/VivID_Epi/results/tables/", recursive = T)
readr::write_csv(x = pvivtbl1df, 
                 path = "~/Documents/GitHub/VivID_Epi/results/tables/pvivtblones_counts.csv",
                 na = "")

readr::write_csv(x = pfaltbl1df, 
                 path = "~/Documents/GitHub/VivID_Epi/results/tables/pfaltblones_counts.csv",
                 na = "")

readr::write_csv(x = casestbl1df, 
                 path = "~/Documents/GitHub/VivID_Epi/results/tables/cases_noncases_tblones_counts.csv",
                 na = "")





readr::write_csv(x = pvivriskfactortable, 
                 path = "~/Documents/GitHub/VivID_Epi/results/tables/pvivriskfactortable_tabletwos.csv",
                 na = "")

readr::write_csv(x = pfalriskfactortable, 
                 path = "~/Documents/GitHub/VivID_Epi/results/tables/pfalriskfactortable_tabletwos.csv",
                na = "")


```

#### N.B. Future Exclusions
The temperatuare covariate is excluded in downstream analyses as altitude was considered an instrumental variable for temperature (as well as being so collinear that we could not untangle them). As a result, only altitude was kept in the DAG and considered for IPTWs.


#### Appendix
##### Cluster Level Prevalences Table (Unweighted Ns)
```{r, results='asis'}

clst %>% 
  dplyr::mutate_if(is.numeric, round, 3) %>% 
  DT::datatable(., extensions='Buttons',
                options = list(
                  searching = T,
                  pageLength = 20,
                  dom = 'Bfrtip', 
                  buttons = c('csv')))

```

##### Cluster Level Prevalences Table (Weighted Ns)
```{r, results='asis'}

clstprev %>% 
  dplyr::mutate_if(is.numeric, round, 3) %>% 
  DT::datatable(., extensions='Buttons',
                options = list(
                  searching = T,
                  pageLength = 20,
                  dom = 'Bfrtip', 
                  buttons = c('csv')))

```



