---
output: html_document
editor_options: 
  chunk_output_type: console
---
# Basic Maps & Spatial Autocorrelation of Malaria Across DRC

```{r, include=FALSE}
knitr::opts_chunk$set(echo = T, warning = F, message = F, eval = T, results = 'hide',
                      fig.align = 'center')

```
```{r}
source("~/Documents/GitHub/VivID_Epi/R/00-functions_basic.R")
source("~/Documents/GitHub/VivID_Epi/R/00-functions_maps.R") 
library(tidyverse)
library(sf)
library(geosphere)
library(spdep)
library(raster)
library(srvyr) #wrap the survey package in dplyr syntax
library(RColorBrewer)


#......................
# Import Data
#......................
load("~/Documents/GitHub/VivID_Epi/data/map_bases/vivid_maps_bases.rda")
dt <- readRDS("~/Documents/GitHub/VivID_Epi/data/derived_data/vividepi_recode_completecases.rds")
DRCprov <- readRDS("~/Documents/GitHub/VivID_Epi/data/map_bases/vivid_DRCprov.rds")
ge <- readRDS(file = "~/Documents/GitHub/VivID_Epi/data/raw_data/dhsdata/VivIDge.RDS")

# need to add back in geometry to dt
gegeoms <- ge %>% 
  dplyr::select(c("hv001", "geometry"))
dt <- dplyr::left_join(dt, gegeoms, by = "hv001")

dtsrvy <- makecd2013survey(survey = dt)

```

## Notes
**N.B. Everyone is weighted the same in the cluster, which results in the same cluster level prevalences whether you consider weights or not**. However, this will results in  slightly different numerator (e.g. $n_numerator$) and denominators between the weighted and unweighted approach. Caution is warranted when reporting weighted versus unweighted Ns and Standard Errors at the cluster-level for this reason. 

## Aggregated Prevalence Maps
```{r}
#---------------------------------------------------------------------- 
# Plasmodium Point Prevalence Maps (Province & Cluster)
#---------------------------------------------------------------------- 

pfldhprov <- prev_point_est_summarizer(design = dtsrvy, maplvl = adm1name, plsmdmspec = pfldh, adm1shp = DRCprov) %>% 
  dplyr::mutate(plsmdmspec = "pfldh", maplvl = "adm1name")
pv18sprov <- prev_point_est_summarizer(design = dtsrvy, maplvl = adm1name, plsmdmspec = pv18s, adm1shp = DRCprov)  %>% 
  dplyr::mutate(plsmdmspec = "pv18s", maplvl = "adm1name")
po18sprov <- prev_point_est_summarizer(design = dtsrvy, maplvl = adm1name, plsmdmspec = po18s, adm1shp = DRCprov) %>% 
  dplyr::mutate(plsmdmspec = "po18s", maplvl = "adm1name")

pfldhclust <- prev_point_est_summarizer(design = dtsrvy, maplvl = hv001, plsmdmspec = pfldh, adm1shp = DRCprov) %>% 
  dplyr::mutate(plsmdmspec = "pfldh", maplvl = "hv001")
pv18sclust <- prev_point_est_summarizer(design = dtsrvy, maplvl = hv001, plsmdmspec = pv18s, adm1shp = DRCprov) %>% 
  dplyr::mutate(plsmdmspec = "pv18s", maplvl = "hv001")
po18sclust <- prev_point_est_summarizer(design = dtsrvy, maplvl = hv001, plsmdmspec = po18s, adm1shp = DRCprov) %>% 
  dplyr::mutate(plsmdmspec = "po18s", maplvl = "hv001")



# bind those to a tibble
mp <- dplyr::bind_rows(pfldhprov, pv18sprov, po18sprov, pfldhclust, pv18sclust, po18sclust) %>% 
  dplyr::group_by(plsmdmspec, maplvl) %>% 
  tidyr::nest()


# this awful hack becuase of this issue https://github.com/tidyverse/dplyr/issues/3483
# we are going down the rabbit hole just to try and make this stupid survey and purr package work. fine for now but return
mp$data <- lapply(list(pfldhprov, pv18sprov, po18sprov, pfldhclust, pv18sclust, po18sclust), function(x) return(x))

#.............................
# Plot Summary/Point Est Maps
#..............................
mp$plots <- pmap(mp, mapplotter)

```

### Province Prevalence Maps
```{r, results='asis'}

cowplot::plot_grid(mp$plots[[1]],  mp$plots[[2]],  mp$plots[[3]],
                  nrow = 1)


jpeg("~/Documents/GitHub/VivID_Epi/results/figures/Province_Prevalence_3x1.jpg",
     heigh = 8, width = 11, units = "in", res=500)
cowplot::plot_grid(mp$plots[[1]],  mp$plots[[2]],  mp$plots[[3]],
                   nrow = 1)
graphics.off()

```

### Cluster Prevalence Maps
```{r, results='asis'}

jpeg("~/Documents/GitHub/VivID_Epi/results/figures/Cluster_Prevalence_3x1.jpg",
     heigh = 8, width = 11, units = "in", res=500)
cowplot::plot_grid(mp$plots[[4]],  mp$plots[[5]],  mp$plots[[6]],
                   nrow = 1)
graphics.off()

cowplot::plot_grid(mp$plots[[4]],  mp$plots[[5]],  mp$plots[[6]],
                   nrow = 1)


```

```{r}
mp.clst <- mp %>% 
  dplyr::filter(maplvl == "hv001") %>% 
  dplyr::ungroup()

```

### Case Count Maps
```{r, results='asis'}
#......................
# Plot Cases
#......................
case_n_maps <- purrr::pmap(mp.clst[,c("data", "plsmdmspec")], casemap_n_plotter)


jpeg("~/Documents/GitHub/VivID_Epi/results/figures/Case_N_ClusterPlots_3x1.jpg",
     heigh = 8, width = 11, units = "in", res=500)
cowplot::plot_grid(case_n_maps[[1]],  case_n_maps[[2]],  case_n_maps[[3]],
                   nrow = 1)
graphics.off()


cowplot::plot_grid(case_n_maps[[1]],  case_n_maps[[2]],  case_n_maps[[3]],
                   nrow = 1)

```

### Point Prevalence (Prettier)

```{r, results='asis'}

caseprevmaps <- purrr::pmap(mp.clst[,c("data", "plsmdmspec")], casemap_prev_plotter)

cowplot::plot_grid(caseprevmaps[[1]],  caseprevmaps[[2]],  caseprevmaps[[3]],
                  nrow = 1)

jpeg("~/Documents/GitHub/VivID_Epi/results/figures/Prevalence_Case_ClusterPlots_3x1.jpg",
     heigh = 8, width = 11, units = "in", res=500)
cowplot::plot_grid(caseprevmaps[[1]],  caseprevmaps[[2]],  caseprevmaps[[3]],
                  nrow = 1)
graphics.off()



```

### Case Plot (Prettier)

```{r}

pvcaseprev <- caseprevmaps[[2]] +
  ggtitle("") +
  prettybasemap_nodrc + 
  theme(
    legend.position = "right",
    legend.text = element_text(face = "bold", angle = 0, vjust = 0.5, hjust = 0.5)
  )


# make world map
DRC <- readRDS("~/Documents/GitHub/VivID_Epi/data/map_bases/gadm/gadm36_COD_0_sp.rds") %>% 
  sf::st_as_sf(.)

bb <- sf::st_bbox(
  sf::st_sf(geom = sf::st_sfc(
    sf::st_point(c(-19, -37)), # left lower
    sf::st_point(c(51, -37)), # right lower
    sf::st_point(c(-19, 38)), # left upper
    sf::st_point(c(51, 38)), # right upper
    crs = sf::st_crs("+proj=longlat +datum=WGS84 +no_defs"))
  ))

africa <- rnaturalearth::ne_countries(scale = "large", returnclass = "sf") %>% 
  dplyr::filter(continent == "Africa") %>% 
  sf::st_crop(., y=bb)


africaplot <- ggplot() + 
  geom_sf(data = africa, fill = "#f0f0f0") +
  geom_sf(data = DRC, fill = "#636363")  +
  coord_sf(datum=NA) +
  theme_bw() + 
  theme(legend.position = "none", 
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.background = element_rect(fill = "white", color = "black", size = 1))



jpeg("~/Documents/GitHub/VivID_Epi/results/figures/Africa_Inset_PvClstPrev.jpg", width = 11, height = 8, units = "in", res = 500)
cowplot::ggdraw() +
  cowplot::draw_plot(pvcaseprev, x = 0, y = 0, width = 1, height = 1, scale = 1) +
  cowplot::draw_plot(africaplot, x = 0.02, y= 0.68, width = 0.35, height = 0.25)
graphics.off()


```

```{r, results='asis'}

cowplot::ggdraw() +
  cowplot::draw_plot(pvcaseprev, x = 0, y = 0, width = 1, height = 1, scale = 1) +
  cowplot::draw_plot(africaplot, x = 0.02, y= 0.68, width = 0.35, height = 0.25)

```

## Spatial Autocorrelation 

### Moran's I by Province
```{r, results='asis'}

#......................
# Make Adjacency Matrix for Pvf
#......................
drcprov <- readRDS("~/Documents/GitHub/VivID_Epi/data/map_bases/vivid_DRCprov.rds")
# https://cran.r-project.org/web/packages/spdep/vignettes/nb.pdf
W.nb <- spdep::poly2nb(sf::as_Spatial(drcprov), row.names = drcprov$adm1name)
W <- spdep::nb2mat(W.nb, style = "B") # binary weights taking values zero or one (only one is recorded)


moran_mc_wrapper <- function(data, listw){
  prev <- data$plsmdprev
  ret <- spdep::moran.mc(x = prev,
                         listw = spdep::mat2listw(listw),
                         alternative = "greater",
                         nsim = 1e5)
  return(ret)
}

#........................
# Moran's I for Prov
#........................
mp.prov <- mp %>% 
  dplyr::filter(maplvl == "adm1name") %>% 
  dplyr::ungroup()

mp.prov$moranIprov <- purrr::map(mp.prov$data, moran_mc_wrapper, listw = W)

moranIprov <- mp.prov %>% 
  dplyr::select(c("plsmdmspec", "moranIprov")) 

moranIprov$Istatistic <- purrr::map(moranIprov$moranIprov, "statistic")
moranIprov$pvalue <- purrr::map(moranIprov$moranIprov, "p.value")

moranIprov <- moranIprov %>% 
  dplyr::select(-c("moranIprov")) %>% 
  tidyr::unnest(cols = c("Istatistic", "pvalue"))

knitr::kable(moranIprov)

```

### Moran's I by Cluster
```{r, results='asis'}

#........................
# Moran's I for Cluster Level
#........................
ge.nosf <- ge
sf::st_geometry(ge.nosf) <- NULL

# note, need to remove three clusters that were not screened for malaria
# one cluster due to no HIV testing in it(? DHS internal) and 
# two clusters lost due to contamination
maldhsclustlist <- unique( dt$hv001 )
ge.nosf <- ge.nosf %>% 
  dplyr::filter(hv001 %in% maldhsclustlist)

# get GC Weight Matrix
gcdist <- ge.nosf %>% 
   dplyr::select(c("longnum", "latnum")) %>% 
  geosphere::distm(x =., fun = geosphere::distGeo) # geodisc approach 
gcdist.inv <- 1/gcdist
diag(gcdist.inv) <- 0

mp.clst$moranIclust <- purrr::map(mp.clst$data, moran_mc_wrapper, listw = gcdist.inv)

moranIclst <- mp.clst %>% 
  dplyr::select(c("plsmdmspec", "moranIclust")) 


moranIclst$Istatistic <- purrr::map(moranIclst$moranIclust, "statistic")
moranIclst$pvalue <- purrr::map(moranIclst$moranIclust, "p.value")

moranIclst <- moranIclst %>% 
  dplyr::select(-c("moranIclust")) %>% 
  tidyr::unnest(cols = c("Istatistic", "pvalue"))

knitr::kable(moranIclst)


```


## Krigged Prevalence Maps
**N.B. Here I have employed an empirical logit transformation and used a "trans-Gaussian" approximation under a MLE framework**. This means that I now assume a model framework of:    
$$\hat{Y}|S(x_i) \sim N(X_i^\intercal \space \beta \space + \space S(x_i), \space \tau^2)$$. Under this formulation, nugget effects are being absorbed by the conditional normal. 
  
```{r}

source("~/Documents/GitHub/VivID_Epi/R/00-functions_maps.R")

pfldhprev <- guass_map_clstr_summarizer(data = dt, plsmdmspec = pfldh, clustgeom = ge) %>% 
  dplyr::mutate(plsmdmspec = "pfldh")
pv18sprev <- guass_map_clstr_summarizer(data = dt, plsmdmspec = pv18s, clustgeom = ge) %>% 
  dplyr::mutate(plsmdmspec = "pv18s")
po18sprev <- guass_map_clstr_summarizer(data = dt, plsmdmspec = po18s, clustgeom = ge) %>% 
  dplyr::mutate(plsmdmspec = "po18s")

# bind those to a tibble
pr <- dplyr::bind_rows(pfldhprev, pv18sprev, po18sprev) %>% 
  dplyr::group_by(plsmdmspec) %>% 
  tidyr::nest()


#.............................
# get prev rasters
#..............................
poly <- cbind(c(17,32,32,12,12), c(-14,-14,6,6,-14)) 
grid.pred <- splancs::gridpts(poly, xs=0.1, ys=0.1)
colnames(grid.pred) <- c("long","lat")

pr$prevrasters <- map(pr$data, 
                      fit_pred_spMLE, outcome = "logitplsmdprev", covar = "1", 
                      long_var = "longnum", lat_var = "latnum",
                      grid.pred = grid.pred, kappa = 0.5, 
                      pred.reps = 1e2)

pr$prevrasterspred <- purrr::map(pr$prevrasters, "pred")

```

```{r, results='asis'}
#.............................
# plot prev rasters
#..............................
prevmaprasterplots <- lapply(pr$prevrasterspred,
                             prevmaprasterplotter, smoothfct = rep(7,3))
prevmaprasterplots.north <- map(prevmaprasterplots, function(x){return(x + prettybasemap_nodrc)})



cowplot::plot_grid(prevmaprasterplots.north[[1]],
                   prevmaprasterplots.north[[2]],
                   prevmaprasterplots.north[[3]],
                  nrow = 1)


jpeg("~/Documents/GitHub/VivID_Epi/results/figures/PrevMap_Plots_3x1.jpg",
     heigh = 8, width = 11, units = "in", res=500)
cowplot::plot_grid(prevmaprasterplots.north[[1]],
                   prevmaprasterplots.north[[2]],
                   prevmaprasterplots.north[[3]],
                  nrow = 1)
graphics.off()


```

## _P. vivax_ vs. Ape Distribution 
```{r, results='asis'}

ape <- readRDS("~/Documents/GitHub/VivID_Epi/data/derived_data/drc_ape.rds")

aperange_nhapv <- 
  caseprevmaps[[2]] +
  geom_sf(data = ape, aes(fill = species), alpha = 0.4) +
  scale_fill_manual("Non-Human \n Ape Range", values = c("#33a02c", "#b3de69", "#8dd3c7", "#80b1d3"))




```

### Permutation Test for _P. vivax_ vs. Ape Distribution 
```{r}
# how many clusters do apes overlap?
ape.range <- sf::st_union(ape$geometry)
ape.clusters <- sf::st_intersection(ge, ape.range)

# how many clusters do chimp and gorillas overlap?
chimpgor.range <- ape %>% 
  dplyr::filter(species != "Pan paniscus") %>% 
  dplyr::select(geometry) %>% 
  sf::st_union(.)
chimpgor.clusters <- sf::st_intersection(ge, chimpgor.range)

```


Data will be simulated by randomly assigning clusters as ape or not territories and then calculating the prevalence of Pv within ape and non-ape regions. 
  
```{r}

run_ape_permutations <- function(dtsrvy18s, n.apeclsts){
  
  clsts <- dtsrvy18s %>% 
    tibble::as_tibble(.) %>% 
    dplyr::select("hv001") %>% 
    dplyr::filter(!duplicated(.)) %>% 
    unlist(.)
  
  apeclsts <- sample(clsts, size = n.apeclsts, replace = F)

  ape.ovrlp.pos <- dtsrvy18s %>% 
    dplyr::filter(hv001 %in% apeclsts) %>% 
    dplyr::summarise(pv18s = srvyr::survey_mean(pv18s)) %>% 
    dplyr::select(-c(dplyr::ends_with("_se")))
  
  ret <- unname(as.vector(ape.ovrlp.pos))
  
  return(ret)

}

sims <- 1e4
pv18s.dt <- dt %>% 
  dplyr::select(c("hv001", "pv18s"))


```
     
There are `r length(ape.clusters)` clusters that overlap with apes and `r length(chimpgor.clusters)` clusters that overlap with chimpanzee and gorillas.

#### All Apes 

```{r, results='asis'}

ape.range.iters <- data.frame(iter = 1:sims)

ape.range.iters$ape_overlap_prev <- purrr::map(ape.range.iters$iter, function(x){
  return( run_ape_permutations(dt18s = pv18s.dt, n.apeclsts = length(ape.clusters)) )
  }) 
  
ape.range.iters$ape_overlap_prev <- unlist(ape.range.iters$ape_overlap_prev )


real.ape.clstrprev <- dt %>% 
  dplyr::filter(hv001 %in% ape.clusters$hv001)

real.ape.clstrprev <- mean(real.ape.clstrprev$pv18s)

hist(ape.range.iters$ape_overlap_prev, breaks = 50, 
     main = "Simulated Pvivax Prevelance \n within Ape Clusters")
abline(v = real.ape.clstrprev, col = "red")



```

Assuming a one-sided test that ape clusters should have more _P. vivax_, we can get a monte-carlo P-value of approximately `r round(mean(ape.range.iters$ape_overlap_prev > real.ape.clstrprev), 2)`. Obviously not significant from plot and maps.


#### Chimpanzee & Gorillas
Note, Bonobos have recently been shown to also harbor _P. vivax-like_ strains but mostly at a concentrated field site, Tshuapa–Lomami–Lualaba (TL2), near the Lomami River [Liu et al. 2018](https://www.nature.com/articles/s41467-017-01798-5)

```{r, results='asis'}

chimpgor.range.iters <- data.frame(iter = 1:sims)

chimpgor.range.iters$chimpgor_overlap_prev <- purrr::map(chimpgor.range.iters$iter, function(x){
  return( run_ape_permutations(dt18s = pv18s.dt, n.apeclsts = length(chimpgor.clusters)) )
}) 

chimpgor.range.iters$chimpgor_overlap_prev <- unlist(chimpgor.range.iters$chimpgor_overlap_prev )


real.chimpgor.clstrprev <- dt %>% 
  dplyr::filter(hv001 %in% chimpgor.clusters$hv001)

real.chimpgor.clstrprev <- mean(real.chimpgor.clstrprev$pv18s)

hist(chimpgor.range.iters$chimpgor_overlap_prev, breaks = 50, 
     main = "Simulated Pvivax Prevelance \n within Chimp & Gor Clusters")
abline(v = real.chimpgor.clstrprev, col = "red")


```

As above, assuming a one-sided test that chimpanzee and gorilla clusters should have more _P. vivax_, we can get a monte-carlo P-value of approximately `r round(mean(chimpgor.range.iters$chimpgor_overlap_prev > real.chimpgor.clstrprev), 2)`. Obviously not significant from plot and maps.


```{r}
#---------------------------------------------- 
# Housekeeping -- save out and write out
#----------------------------------------------- 
 
saveRDS(mp, file = "~/Documents/GitHub/VivID_Epi/data/derived_data/basic_cluster_mapping_data.rds")


provmaps <- mp$plots[1:3]

save(provmaps, caseprevmaps, case_n_maps, aperange_nhapv,
      file = "~/Documents/GitHub/VivID_Epi/results/basic_maps_results.rda")

```

```{r}

##############################
# Ape Overlap
##############################
jpeg("~/Documents/GitHub/VivID_Epi/results/figures/pv-ape-overlap-crude_maps1x1.jpg", width = 11, height = 8, units = "in", res = 500)
aperange_nhapv + prettybasemap_nodrc
graphics.off()

```

```{r, results = 'asis', fig.width= 12, fig.height=12}
aperange_nhapv + prettybasemap_nodrc
```


#### More Maps

```{r}

############################################################
#########               MORE MAPS                  ######### 
############################################################
provmaps_lrg <- map(provmaps, function(x){return(x + prettybasemap_nodrc_nonorth)})
caseprevmaps_lrg <- map(caseprevmaps, function(x){return(x + prettybasemap_nodrc_nonorth)})
case_n_maps_lrg <- map(case_n_maps, function(x){return(x + prettybasemap_nodrc_nonorth)})
prevmaprasterplots_lrg <- map(prevmaprasterplots, function(x){return(x + prettybasemap_nodrc_nonorth)})


##############################
# Pf, Pv, Po All together
##############################
jpeg("~/Documents/GitHub/VivID_Epi/results/figures/pv-pf-po_crude_maps3x3.jpg", width = 11, height = 8, units = "in", res = 500)
gridExtra::grid.arrange(
  provmaps_lrg[[1]], caseprevmaps_lrg[[1]], prevmaprasterplots_lrg[[1]],
  provmaps_lrg[[2]], caseprevmaps_lrg[[2]], prevmaprasterplots_lrg[[2]],
  provmaps_lrg[[3]], caseprevmaps_lrg[[3]], prevmaprasterplots_lrg[[3]],
  ncol=3, top=grid::textGrob("Malaria Species #Prevalence in CD2013 DHS", 
                             gp=grid::gpar(fontsize=15, fontfamily = "Arial", fontface = "bold"))) 

graphics.off()
```

```{r, results = 'asis', fig.width= 12, fig.height=12}

gridExtra::grid.arrange(
  provmaps_lrg[[1]], caseprevmaps_lrg[[1]], prevmaprasterplots_lrg[[1]],
  provmaps_lrg[[2]], caseprevmaps_lrg[[2]], prevmaprasterplots_lrg[[2]],
  provmaps_lrg[[3]], caseprevmaps_lrg[[3]], prevmaprasterplots_lrg[[3]],
  ncol=3, top=grid::textGrob("Malaria Species Prevalence in CD2013 DHS", 
                             gp=grid::gpar(fontsize=15, fontfamily = "Arial", fontface = "bold"))) 
```

```{r}
##############################
# Just Pv 
##############################
jpeg("~/Documents/GitHub/VivID_Epi/results/figures/pv-crude_maps2x2.jpg", width = 11, height = 8, units = "in", res = 500)
gridExtra::grid.arrange(
  provmaps_lrg[[2]], case_n_maps_lrg[[2]],
  caseprevmaps_lrg[[2]], prevmaprasterplots_lrg[[2]], 
  ncol=2, top=grid::textGrob("P. vivax Prevalence in CD2013 DHS", 
                             gp=grid::gpar(fontsize=15, fontfamily = "Arial", fontface = "bold"))) 

graphics.off()

```

```{r, results = 'asis', fig.width= 12, fig.height=12}

gridExtra::grid.arrange(
  provmaps_lrg[[2]], case_n_maps_lrg[[2]],
  caseprevmaps_lrg[[2]], prevmaprasterplots_lrg[[2]], 
  ncol=2, top=grid::textGrob("P. vivax Prevalence in CD2013 DHS", 
                             gp=grid::gpar(fontsize=15, fontfamily = "Arial", fontface = "bold"))) 

```

```{r, results = 'asis', fig.width= 12, fig.height=12}
gridExtra::grid.arrange(
  provmaps_lrg[[2]], case_n_maps_lrg[[2]],
  caseprevmaps_lrg[[2]], prevmaprasterplots_lrg[[2]], 
  ncol=2, top=grid::textGrob("P. vivax Prevalence in CD2013 DHS", 
                             gp=grid::gpar(fontsize=15, fontfamily = "Arial", fontface = "bold"))) 

```

```{r}

pvclst.dat <- mp.clst %>% 
  dplyr::filter(plsmdmspec == "pv18s") %>% 
  dplyr::select(c("data"))
pvclst.dat <- pvclst.dat$data[[1]] %>%  # can't unnest geometry 
  dplyr::filter(plsmdn > 5)


jpeg("~/Documents/GitHub/VivID_Epi/results/figures/pv-case_prev_ggrepel_counts.jpg", width = 11, height = 8, units = "in", res = 500)
caseprevmaps_lrg[[2]] + ggrepel::geom_label_repel(data = pvclst.dat,
                                                  aes(x = longnum, y = latnum, label = plsmdn)) +
  ggtitle("Labeled with Cluster Case Counts > 5")
graphics.off()


```


```{r, results='asis'}

caseprevmaps_lrg[[2]] + ggrepel::geom_label_repel(data = pvclst.dat,
                                                  aes(x = longnum, y = latnum, label = plsmdn)) +
  ggtitle("Labeled with Cluster Case Counts > 5")

```

```{r}

##############################
# Pf, Pv, together
##############################
pfprevmap <-  prevmaprasterplots_lrg[[1]] +
  ggtitle(expression(bolditalic("P. falciparum"))) +
  prettybasemap_nodrc + 
  theme(
    legend.position = "right",
    legend.text = element_text(face = "bold", angle = 0, vjust = 0.5, hjust = 0.5)
  )

pvprevmap <-  prevmaprasterplots_lrg[[2]] +
  ggtitle(expression(bolditalic("P. vivax"))) +
  prettybasemap_nodrc + 
  theme(
    legend.position = "right",
    legend.text = element_text(face = "bold", angle = 0, vjust = 0.5, hjust = 0.5)
  )

jpeg("~/Documents/GitHub/VivID_Epi/results/figures/pv-pf-prevmap2x2.jpg", width = 11, height = 8, units = "in", res = 500)
cowplot::plot_grid(pfprevmap, 
                   pvprevmap, 
                   nrow = 1)
graphics.off()

```

```{r, results = 'asis'}

cowplot::plot_grid(pfprevmap, 
                   pvprevmap, 
                   nrow = 1)


```


