---
output: html_document
editor_options: 
  chunk_output_type: console
---
# Basic Maps & Spatial Autocorrelation of Malaria Across DRC

```{r, include=FALSE}
knitr::opts_chunk$set(echo = T, warning = F, message = F, eval = T, results = 'hide',
                      fig.align = 'center')
knitr::opts_knit$set(root.dir = here::here())


```
```{r}
source("R/00-functions_basic.R")
source("R/00-functions_maps.R") 
library(tidyverse)
library(sf)
library(geosphere)
library(spdep)
library(raster)
library(srvyr) #wrap the survey package in dplyr syntax
library(RColorBrewer)
set.seed(48)

#......................
# Import Data
#......................
load("data/map_bases/vivid_maps_bases.rda")
dt <- readRDS("data/derived_data/vividepi_recode_completecases.rds")
DRCprov <- readRDS("data/map_bases/vivid_DRCprov.rds")
ge <- readRDS(file = "data/raw_data/dhsdata/VivIDge.RDS")

# need to add back in geometry to dt
gegeoms <- ge %>% 
  dplyr::select(c("hv001", "geometry"))
dt <- dplyr::left_join(dt, gegeoms, by = "hv001")

dtsrvy <- makecd2013survey(survey = dt)

```

## Notes
**N.B. Everyone is weighted the same in the cluster, which results in the same cluster level prevalences whether you consider weights or not**. However, this will results in  slightly different numerator (e.g. $n_numerator$) and denominators between the weighted and unweighted approach. Caution is warranted when reporting weighted versus unweighted Ns and Standard Errors at the cluster-level for this reason. 

## Aggregated Prevalence Maps
```{r}
#---------------------------------------------------------------------- 
# Plasmodium Point Prevalence Maps (Province & Cluster)
#---------------------------------------------------------------------- 

pfldhprov <- prev_point_est_summarizer(design = dtsrvy, maplvl = adm1name, plsmdmspec = pfldh, adm1shp = DRCprov) %>% 
  dplyr::mutate(plsmdmspec = "pfldh", maplvl = "adm1name")
pv18sprov <- prev_point_est_summarizer(design = dtsrvy, maplvl = adm1name, plsmdmspec = pv18s, adm1shp = DRCprov)  %>% 
  dplyr::mutate(plsmdmspec = "pv18s", maplvl = "adm1name")
po18sprov <- prev_point_est_summarizer(design = dtsrvy, maplvl = adm1name, plsmdmspec = po18s, adm1shp = DRCprov) %>% 
  dplyr::mutate(plsmdmspec = "po18s", maplvl = "adm1name")

pfldhclust <- prev_point_est_summarizer(design = dtsrvy, maplvl = hv001, plsmdmspec = pfldh, adm1shp = DRCprov) %>% 
  dplyr::mutate(plsmdmspec = "pfldh", maplvl = "hv001")
pv18sclust <- prev_point_est_summarizer(design = dtsrvy, maplvl = hv001, plsmdmspec = pv18s, adm1shp = DRCprov) %>% 
  dplyr::mutate(plsmdmspec = "pv18s", maplvl = "hv001")
po18sclust <- prev_point_est_summarizer(design = dtsrvy, maplvl = hv001, plsmdmspec = po18s, adm1shp = DRCprov) %>% 
  dplyr::mutate(plsmdmspec = "po18s", maplvl = "hv001")



# bind those to a tibble
mp <- dplyr::bind_rows(pfldhprov, pv18sprov, po18sprov, pfldhclust, pv18sclust, po18sclust) %>% 
  dplyr::group_by(plsmdmspec, maplvl) %>% 
  tidyr::nest()


# this awful hack becuase of this issue https://github.com/tidyverse/dplyr/issues/3483
# we are going down the rabbit hole just to try and make this stupid survey and purr package work. fine for now but return
mp$data <- lapply(list(pfldhprov, pv18sprov, po18sprov, pfldhclust, pv18sclust, po18sclust), function(x) return(x))

#.............................
# Plot Summary/Point Est Maps
#..............................
mp$plots <- pmap(mp, mapplotter)

```

### Province Prevalence Maps
```{r, results='asis'}

cowplot::plot_grid(mp$plots[[1]],  mp$plots[[2]],  mp$plots[[3]],
                  nrow = 1)

```

```{r}
jpeg("results/figures/Province_Prevalence_3x1.jpg",
     heigh = 8, width = 11, units = "in", res=500)
cowplot::plot_grid(mp$plots[[1]],  mp$plots[[2]],  mp$plots[[3]],
                   nrow = 1)
graphics.off()

```

### Cluster Prevalence Maps
```{r, results='asis'}
cowplot::plot_grid(mp$plots[[4]],  mp$plots[[5]],  mp$plots[[6]],
                   nrow = 1)
```

```{r}
jpeg("results/figures/Cluster_Prevalence_3x1.jpg",
     heigh = 8, width = 11, units = "in", res=500)
cowplot::plot_grid(mp$plots[[4]],  mp$plots[[5]],  mp$plots[[6]],
                   nrow = 1)
graphics.off()

```

```{r}
mp.clst <- mp %>% 
  dplyr::filter(maplvl == "hv001") %>% 
  dplyr::ungroup()

```

### Case Count Maps
```{r}
#......................
# Plot Cases
#......................
case_n_maps <- purrr::pmap(mp.clst[,c("data", "plsmdmspec")], casemap_n_plotter)


jpeg("results/figures/Case_N_ClusterPlots_3x1.jpg",
     heigh = 8, width = 11, units = "in", res=500)
cowplot::plot_grid(case_n_maps[[1]],  case_n_maps[[2]],  case_n_maps[[3]],
                   nrow = 1)
graphics.off()

```

```{r, results='asis'}
cowplot::plot_grid(case_n_maps[[1]],  case_n_maps[[2]],  case_n_maps[[3]],
                   nrow = 1)

```

### Point Prevalence (Prettier)

```{r}

caseprevmaps <- purrr::pmap(mp.clst[,c("data", "plsmdmspec")], casemap_prev_plotter)

jpeg("results/figures/Prevalence_Case_ClusterPlots_3x1.jpg",
     heigh = 8, width = 11, units = "in", res=500)
cowplot::plot_grid(caseprevmaps[[1]],  caseprevmaps[[2]],  caseprevmaps[[3]],
                  nrow = 1)
graphics.off()

```

```{r, results='asis'}
cowplot::plot_grid(caseprevmaps[[1]],  caseprevmaps[[2]],  caseprevmaps[[3]],
                  nrow = 1)
```

### Case Plot (Prettier)

```{r}

pvcaseprev <- mp.clst[,c("data", "plsmdmspec")] %>% 
  dplyr::filter(plsmdmspec == "pv18s") 
pvcaseprev <- pvcaseprev$data[[1]]

pos <- pvcaseprev %>% 
    dplyr::filter(plsmdprev > 0)
neg <- pvcaseprev %>% 
    dplyr::filter(plsmdprev == 0)
  
pvret <- ggplot() + 
  geom_sf(data = DRCprov, color = "#737373", fill = "#525252") +
  geom_sf(data = neg, aes(size = n), shape = 4, show.legend = F, colour = "#f0f0f0") +
  geom_sf(data = pos, aes(colour = plsmdprev, size = n), alpha = 0.9) +
  scale_color_distiller("Prevalence", type = "div", palette = "RdYlBu") +
  scale_size(guide = 'none') +
  coord_sf(datum=NA) + # to get rid of gridlines
  vivid_theme +
  prettybasemap_nodrc_dark +
  theme(axis.text = element_blank(),
        axis.line = element_blank(), 
        axis.title = element_blank(),
        legend.position = "right",
        legend.text = element_text(face = "bold", angle = 0, vjust = 0.5, hjust = 0.5)) 


# make world map
DRC <- readRDS("data/map_bases/gadm/gadm36_COD_0_sp.rds") %>% 
  sf::st_as_sf(.)

bb <- sf::st_bbox(
  sf::st_sf(geom = sf::st_sfc(
    sf::st_point(c(-19, -37)), # left lower
    sf::st_point(c(51, -37)), # right lower
    sf::st_point(c(-19, 38)), # left upper
    sf::st_point(c(51, 38)), # right upper
    crs = sf::st_crs("+proj=longlat +datum=WGS84 +no_defs"))
  ))

africa <- rnaturalearth::ne_countries(scale = "large", returnclass = "sf") %>% 
  dplyr::filter(continent == "Africa") %>% 
  sf::st_crop(., y=bb)


africaplot <- ggplot() + 
  geom_sf(data = africa, fill = "#f0f0f0") +
  geom_sf(data = DRC, fill = "#636363")  +
  coord_sf(datum=NA) +
  theme_bw() + 
  theme(legend.position = "none", 
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.background = element_rect(fill = "white", color = "black", size = 1))



jpeg("results/figures/Africa_Inset_PvClstPrev_dark.jpg", width = 11, height = 8, units = "in", res = 500)
cowplot::ggdraw() +
  cowplot::draw_plot(pvret, x = 0, y = 0, width = 1, height = 1, scale = 1) +
  cowplot::draw_plot(africaplot, x = 0.02, y= 0.68, width = 0.35, height = 0.25)
graphics.off()


```

```{r, results='asis'}

cowplot::ggdraw() +
  cowplot::draw_plot(pvret, x = 0, y = 0, width = 1, height = 1, scale = 1) +
  cowplot::draw_plot(africaplot, x = 0.02, y= 0.68, width = 0.35, height = 0.25)

```

## Spatial Autocorrelation 

### Moran's I by Province
```{r, results='asis'}

#......................
# Make Adjacency Matrix for Pvf
#......................
drcprov <- readRDS("data/map_bases/vivid_DRCprov.rds")
# https://cran.r-project.org/web/packages/spdep/vignettes/nb.pdf
W.nb <- spdep::poly2nb(sf::as_Spatial(drcprov), row.names = drcprov$adm1name)
W <- spdep::nb2mat(W.nb, style = "B") # binary weights taking values zero or one (only one is recorded)


moran_mc_wrapper <- function(data, listw){
  prev <- data$plsmdprev
  ret <- spdep::moran.mc(x = prev,
                         listw = spdep::mat2listw(listw),
                         alternative = "greater",
                         nsim = 1e5)
  return(ret)
}

#........................
# Moran's I for Prov
#........................
mp.prov <- mp %>% 
  dplyr::filter(maplvl == "adm1name") %>% 
  dplyr::ungroup()

mp.prov$moranIprov <- purrr::map(mp.prov$data, moran_mc_wrapper, listw = W)

moranIprov <- mp.prov %>% 
  dplyr::select(c("plsmdmspec", "moranIprov")) 

moranIprov$Istatistic <- purrr::map(moranIprov$moranIprov, "statistic")
moranIprov$pvalue <- purrr::map(moranIprov$moranIprov, "p.value")

moranIprov <- moranIprov %>% 
  dplyr::select(-c("moranIprov")) %>% 
  tidyr::unnest(cols = c("Istatistic", "pvalue"))

knitr::kable(moranIprov)

```

### Moran's I by Cluster
```{r, results='asis'}

#........................
# Moran's I for Cluster Level
#........................
ge.nosf <- ge
sf::st_geometry(ge.nosf) <- NULL

# note, need to remove three clusters that were not screened for malaria
# one cluster due to no HIV testing in it(? DHS internal) and 
# two clusters lost due to contamination
maldhsclustlist <- unique( dt$hv001 )
ge.clst <- ge %>% 
  dplyr::filter(hv001 %in% maldhsclustlist)

# get GC Weight Matrix
gcdist <- ge.clst %>% 
   dplyr::select(c("longnum", "latnum")) %>% 
  sf::st_distance(x = .,
                  which = "Great Circle")

gcdist  <- apply(gcdist, 2, as.numeric) # drop units
gcdist.inv <- 1/gcdist
diag(gcdist.inv) <- 0

mp.clst$moranIclust <- purrr::map(mp.clst$data, 
                                  moran_mc_wrapper, 
                                  listw = gcdist.inv)

moranIclst <- mp.clst %>% 
  dplyr::select(c("plsmdmspec", "moranIclust")) 


moranIclst$Istatistic <- purrr::map(moranIclst$moranIclust, "statistic")
moranIclst$pvalue <- purrr::map(moranIclst$moranIclust, "p.value")

moranIclst <- moranIclst %>% 
  dplyr::select(-c("moranIclust")) %>% 
  tidyr::unnest(cols = c("Istatistic", "pvalue"))

knitr::kable(moranIclst)


```


## Krigged Prevalence Maps
**N.B. Here I have employed an empirical logit transformation and used a "trans-Gaussian" approximation under a MLE framework**. This means that I now assume a model framework of:    
$$\hat{Y}|S(x_i) \sim N(X_i^\intercal \space \beta \space + \space S(x_i), \space \tau^2)$$    
Under this formulation, nugget effects are being absorbed by the conditional normal. 
  
```{r}

source("R/00-functions_maps.R")

pfldhprev <- guass_map_clstr_summarizer(data = dt, plsmdmspec = pfldh, clustgeom = ge) %>% 
  dplyr::mutate(plsmdmspec = "pfldh")
pv18sprev <- guass_map_clstr_summarizer(data = dt, plsmdmspec = pv18s, clustgeom = ge) %>% 
  dplyr::mutate(plsmdmspec = "pv18s")
po18sprev <- guass_map_clstr_summarizer(data = dt, plsmdmspec = po18s, clustgeom = ge) %>% 
  dplyr::mutate(plsmdmspec = "po18s")

# bind those to a tibble
pr <- dplyr::bind_rows(pfldhprev, pv18sprev, po18sprev) %>% 
  dplyr::group_by(plsmdmspec) %>% 
  tidyr::nest()


#.............................
# get prev rasters
#..............................
poly <- cbind(c(17,32,32,12,12), c(-14,-14,6,6,-14)) 
grid.pred <- splancs::gridpts(poly, xs=0.1, ys=0.1)
colnames(grid.pred) <- c("long","lat")

pr$prevrasters <- map(pr$data, 
                      fit_pred_spMLE, outcome = "logitplsmdprev", covar = "1", 
                      long_var = "longnum", lat_var = "latnum",
                      grid.pred = grid.pred, kappa = 0.5, 
                      pred.reps = 1e2)

pr$prevrasterspred <- purrr::map(pr$prevrasters, "pred")

```

```{r, results='asis'}
#.............................
# plot prev rasters
#..............................
prevmaprasterplots <- lapply(pr$prevrasterspred,
                             prevmaprasterplotter, smoothfct = rep(7,3))
prevmaprasterplots.north <- map(prevmaprasterplots, function(x){return(x + smpl_base_map)})



cowplot::plot_grid(prevmaprasterplots.north[[1]],
                   prevmaprasterplots.north[[2]],
                   prevmaprasterplots.north[[3]],
                  nrow = 1)


jpeg("results/figures/PrevMap_Plots_3x1.jpg",
     heigh = 8, width = 11, units = "in", res=500)
cowplot::plot_grid(prevmaprasterplots.north[[1]],
                   prevmaprasterplots.north[[2]],
                   prevmaprasterplots.north[[3]],
                  nrow = 1)
graphics.off()


```
**Order is Pf, Pv, Po**.

#### More Maps

```{r}

############################################################
#########               MORE MAPS                  ######### 
############################################################
provmaps_lrg <- map(provmaps, function(x){return(x + smpl_base_map)})
caseprevmaps_lrg <- map(caseprevmaps, function(x){return(x + smpl_base_map)})
case_n_maps_lrg <- map(case_n_maps, function(x){return(x + smpl_base_map)})
prevmaprasterplots_lrg <- map(prevmaprasterplots, function(x){return(x + smpl_base_map)})


##############################
# Pf, Pv, Po All together
##############################
jpeg("results/figures/pv-pf-po_crude_maps3x3.jpg", width = 11, height = 8, units = "in", res = 500)
gridExtra::grid.arrange(
  provmaps_lrg[[1]], caseprevmaps_lrg[[1]], prevmaprasterplots_lrg[[1]],
  provmaps_lrg[[2]], caseprevmaps_lrg[[2]], prevmaprasterplots_lrg[[2]],
  provmaps_lrg[[3]], caseprevmaps_lrg[[3]], prevmaprasterplots_lrg[[3]],
  ncol=3, top=grid::textGrob("Malaria Species #Prevalence in CD2013 DHS", 
                             gp=grid::gpar(fontsize=15, fontfamily = "Arial", fontface = "bold"))) 

graphics.off()
```

```{r, results = 'asis', fig.width= 12, fig.height=12}

gridExtra::grid.arrange(
  provmaps_lrg[[1]], caseprevmaps_lrg[[1]], prevmaprasterplots_lrg[[1]],
  provmaps_lrg[[2]], caseprevmaps_lrg[[2]], prevmaprasterplots_lrg[[2]],
  provmaps_lrg[[3]], caseprevmaps_lrg[[3]], prevmaprasterplots_lrg[[3]],
  ncol=3, top=grid::textGrob("Malaria Species Prevalence in CD2013 DHS", 
                             gp=grid::gpar(fontsize=15, fontfamily = "Arial", fontface = "bold"))) 
```

```{r}
##############################
# Just Pv 
##############################
jpeg("results/figures/pv-crude_maps2x2.jpg", width = 11, height = 8, units = "in", res = 500)
gridExtra::grid.arrange(
  provmaps_lrg[[2]], case_n_maps_lrg[[2]],
  caseprevmaps_lrg[[2]], prevmaprasterplots_lrg[[2]], 
  ncol=2, top=grid::textGrob("P. vivax Prevalence in CD2013 DHS", 
                             gp=grid::gpar(fontsize=15, fontfamily = "Arial", fontface = "bold"))) 

graphics.off()

```

```{r, results = 'asis', fig.width= 12, fig.height=12}

gridExtra::grid.arrange(
  provmaps_lrg[[2]], case_n_maps_lrg[[2]],
  caseprevmaps_lrg[[2]], prevmaprasterplots_lrg[[2]], 
  ncol=2, top=grid::textGrob("P. vivax Prevalence in CD2013 DHS", 
                             gp=grid::gpar(fontsize=15, fontfamily = "Arial", fontface = "bold"))) 

```

```{r, results = 'asis', fig.width= 12, fig.height=12}
gridExtra::grid.arrange(
  provmaps_lrg[[2]], case_n_maps_lrg[[2]],
  caseprevmaps_lrg[[2]], prevmaprasterplots_lrg[[2]], 
  ncol=2, top=grid::textGrob("P. vivax Prevalence in CD2013 DHS", 
                             gp=grid::gpar(fontsize=15, fontfamily = "Arial", fontface = "bold"))) 

```

```{r}

pvclst.dat <- mp.clst %>% 
  dplyr::filter(plsmdmspec == "pv18s") %>% 
  dplyr::select(c("data"))
pvclst.dat <- pvclst.dat$data[[1]] %>%  # can't unnest geometry 
  dplyr::filter(plsmdn > 5)


jpeg("results/figures/pv-case_prev_ggrepel_counts.jpg", width = 11, height = 8, units = "in", res = 500)
caseprevmaps_lrg[[2]] + ggrepel::geom_label_repel(data = pvclst.dat,
                                                  aes(x = longnum, y = latnum, label = plsmdn)) +
  ggtitle("Labeled with Cluster Case Counts > 5")
graphics.off()


```


```{r, results='asis'}

caseprevmaps_lrg[[2]] + ggrepel::geom_label_repel(data = pvclst.dat,
                                                  aes(x = longnum, y = latnum, label = plsmdn)) +
  ggtitle("Labeled with Cluster Case Counts > 5")

```

```{r}

##############################
# Pf, Pv, together
##############################
pfprevmap <-  prevmaprasterplots_lrg[[1]] +
  ggtitle(expression(bolditalic("P. falciparum"))) +
  smpl_base_map + 
  theme(
    legend.position = "right",
    legend.text = element_text(face = "bold", angle = 0, vjust = 0.5, hjust = 0.5)
  )

pvprevmap <-  prevmaprasterplots_lrg[[2]] +
  ggtitle(expression(bolditalic("P. vivax"))) +
  smpl_base_map + 
  theme(
    legend.position = "right",
    legend.text = element_text(face = "bold", angle = 0, vjust = 0.5, hjust = 0.5)
  )

jpeg("results/figures/pv-pf-prevmap2x2.jpg", width = 11, height = 8, units = "in", res = 500)
cowplot::plot_grid(pfprevmap, 
                   pvprevmap, 
                   nrow = 1)
graphics.off()

```

```{r, results = 'asis'}

cowplot::plot_grid(pfprevmap, 
                   pvprevmap, 
                   nrow = 1)


```


```{r}

##############################
# Pf nice
##############################
drccites <- readxl::read_excel("data/map_bases/DRC_city_coordinates.xlsx") %>% 
  dplyr::mutate(latnum = as.numeric( stringr::str_split_fixed(coordinates, ",", n=2)[,1] ),
                longnum = as.numeric( stringr::str_split_fixed(coordinates, ",", n=2)[,2] ) 
                )

pfprevmap <- pfprevmap  +
  geom_point(data = drccites, aes(x = longnum, y=latnum)) + 
  geom_text(data = drccites, aes(label = city, x = longnum, y=latnum), 
            hjust = 0.5, vjust = 0.5, nudge_y = 0.3, fontface = "bold") +
  theme(legend.position = "right",
        legend.title = element_text(size = 13, face = "bold", angle = 0, vjust = 0.5, hjust = 0.5),
        legend.text = element_text(size = 12, face = "bold", angle = 0))


jpeg("results/figures/pf-prevmap_nice.jpg", width = 11, height = 8, units = "in", res = 500)
plot(pfprevmap)
graphics.off()

```

```{r, results = 'asis'}
plot(pfprevmap)
```


```{r}
# make sample location plots
clstcounts <- dtsrvy %>% 
  dplyr::group_by(hv001) %>% 
  dplyr::mutate(count = 1) %>% 
  dplyr::summarise( 
    n = srvyr::survey_total(count)
    )
clstcounts <- dplyr::left_join(clstcounts, ge, by = "hv001")

clstcountsplot <- ggplot() + 
  geom_sf(data = DRCprov, fill = "#e5f5e0", color = "#969696") +
  geom_point(data = clstcounts, aes(x = longnum, y = latnum, size = n), fill = "#252525", shape = 4, alpha = 0.5, show.legend = F) +
  prettybasemap_nodrc


jpeg("results/figures/Africa_Inset_clsts.jpg", width = 11, height = 8, units = "in", res = 500)
cowplot::ggdraw() +
  cowplot::draw_plot(clstcountsplot, x = 0, y = 0, width = 1, height = 1, scale = 1) +
  cowplot::draw_plot(africaplot, x = 0.02, y= 0.68, width = 0.35, height = 0.25)
graphics.off()


```

```{r, results='asis'}

cowplot::ggdraw() +
  cowplot::draw_plot(clstcountsplot, x = 0, y = 0, width = 1, height = 1, scale = 1) +
  cowplot::draw_plot(africaplot, x = 0.02, y= 0.68, width = 0.35, height = 0.25)

```

